---
title: "Multiyear RECS data handling"
author: "James Woods"
date: "07/16/2015"
output: html_document
---

```{r}
#All2009 <- read.csv("2009/recs2009_public.csv")

library(readr)
All2009 <- read_csv("2009/recs2009_public.csv")

#All2005 <- read.csv("2005/RECS05alldata.csv")
All2005 <- read_csv("2005/RECS05alldata.csv")
```
Those two are simple but the 2001 data comes in many parts

```{r}
publicuse102001<-read_csv("2001/publicuse102001.csv" )  
publicuse2001<-read_csv("2001/publicuse2001.csv" )   
publicuse42001<-read_csv("2001/publicuse42001.csv" )  
publicuse72001<-read_csv("2001/publicuse72001.csv" )
publicuse112001<-read_csv("2001/publicuse112001.csv" )  
publicuse22001<-read_csv("2001/publicuse22001.csv" )  
publicuse52001<-read_csv("2001/publicuse52001.csv" )  
publicuse82001<-read_csv("2001/publicuse82001.csv" )
publicuse122001<-read_csv("2001/publicuse122001.csv" ) 
publicuse32001<-read_csv("2001/publicuse32001.csv" )
publicuse62001<-read_csv("2001/publicuse62001.csv" )  
publicuse92001<-read_csv("2001/publicuse92001.csv" )

#DOEID is the merge key
library(reshape)
All2001<-merge_recurse(list(publicuse102001,publicuse112001,publicuse122001,publicuse2001,publicuse22001,publicuse32001,publicuse42001,publicuse52001,publicuse62001,publicuse72001,publicuse82001,publicuse92001))

library(stringr)
#Clean up name space
rm(list=c('publicuse102001','publicuse112001','publicuse122001','publicuse2001','publicuse22001','publicuse32001','publicuse42001','publicuse52001','publicuse62001','publicuse72001','publicuse82001','publicuse92001'))



```

# RECS 2009

Here is a list of the variables I would like from the 2009 RECS.  Include the imputation flag field, they start with a Z for all these variables.  For example, ZYEARMADE is for when they have to impute the variable YEARMADE.

There are some R models in RecodeScratch.R

Formatting ugly to keep the list easy to use.

This is just some example code.  Now commented out.
```{r}
# summary(All2009$DOEID)
# 
# All2009$DOEID<-as.factor(All2009$DOEID)  
# 
# library(plyr)
# #Region
# summary(All2009$REGIONC)
# table(All2009$REGIONC)
# 
# All2009$REGIONC<-revalue(as.factor(All2009$REGIONC),c("1"="NE", "2"="MidWest","3"="South","4"="West"))
# 
# #All2009$REGIONC[1:20]
# All2009[1:2,1:10]
# 
# 
# #Bedrooms
# summary(All2009$BEDROOMS)
# All2009$BEDROOMS[All2009$BEDROOMS==-2]<-NA
# All2009$BEDROOMS[All2009$BEDROOMS==-2]

```


DOEID
REGIONC
DIVISION
REPORTABLE_DOMAIN
TYPEHUQ
NWEIGHT
HDD65
CDD65
Climate_Region_Pub
AIA_Zone
METROMICRO
UR
KOWNRENT
CONDCOOP
YEARMADE
YEARMADERANGE
OCCUPYYRANGE
CONVERSION
ORIG1FAM
LOOKLIKE
NUMFLRS
NUMAPTS
NAPTFLRS
STORIES
TYPEHUQ4
BEDROOMS
NCOMBATH
NHAFBATH
OTHROOMS
TOTROOMS
STOVEN
STOVENFUEL
STOVE
STOVEFUEL
OVEN
OVENFUEL
OVENUSE
MICRO
AMTMICRO
OUTGRILL
OUTGRILLFUEL
TOASTER
NUMMEAL
FUELFOOD
NUMFRIG
TYPERFR1
SIZRFRI1
REFRIGT1
ICE
AGERFRI1
ESFRIG
REPLCFRI
TYPERFR2
SIZRFRI2
MONRFRI2
AGERFRI2
SEPFREEZ
NUMFREEZ
UPRTFRZR
SIZFREEZ
REPLCFRZ
UPRTFRZR2
SIZFREEZ2
AGEFRZR2
DISHWASH
DWASHUSE
AGEDW
ESDISHW
REPLCDW
CWASHER
TOPFRONT
WASHLOAD
WASHTEMP
RNSETEMP
AGECWASH
ESCWASH
DRYER
DRYRFUEL
DRYRUSE
AGECDRYER
TVCOLOR
TVSIZE1
TVTYPE1
CABLESAT1
COMBODVR1
DVR1
DIGITSTB1
PLAYSTA1
COMBOVCRDVD1
VCR1
DVD1
TVAUDIOSYS1
OTHERSTB1
TVONWD1
TVONWDWATCH1
TVONWE1
TVONWEWATCH1
TVSIZE2
TVTYPE2
CABLESAT2
COMBODVR2
DVR2
DIGITSTB2
PLAYSTA2
COMBOVCRDVD2
VCR2
DVD2
TVAUDIOSYS2
OTHERSTB2
TVONWD2
TVONWDWATCH2
TVONWE2
TVONWEWATCH2
COMPUTER
NUMPC
PCTYPE1
MONITOR1
TIMEON1
PCONOFF1
PCSLEEP1
PCTYPE2
MONITOR2
TIMEON2
PCONOFF2
PCSLEEP2
INTERNET
INDIALUP
INDSL
INCABLE
INSATEL
INWIRELESS
WELLPUMP
DIPSTICK
SWAMPCOL
AQUARIUM
BATTOOLS
BATCHRG
CHRGPLGT
ELECDEV
ELECCHRG
CHRGPLGE
HEATHOME
DNTHEAT
EQUIPNOHEAT
FUELNOHEAT
EQUIPM
FUELHEAT
EQUIPAGE
REPLCHT
HEATOTH
EQUIPAUX
REVERSE
WARMAIR
FURNFUEL
STEAMR
RADFUEL
PERMELEC
PIPELESS
PIPEFUEL
ROOMHEAT
RMHTFUEL
WOODKILN
HSFUEL
CARRYEL
CARRYKER
CHIMNEY
FPFUEL
RANGE
RNGFUEL
DIFEQUIP
DIFFUEL
EQMAMT
HEATROOM
THERMAIN
NUMTHERM
PROTHERM
AUTOHEATNITE
AUTOHEATDAY
TEMPHOME
TEMPGONE
TEMPNITE
MOISTURE
USEMOISTURE
NUMH2ONOTNK
NUMH2OHTRS
H2OTYPE1
FUELH2O
WHEATOTH
WHEATSIZ
WHEATAGE
WHEATBKT
H2OTYPE2
FUELH2O2
WHEATSIZ2
WHEATAGE2
AIRCOND
DNTAC
COOLTYPENOAC
COOLTYPE
DUCTS
CENACHP
ACOTHERS
AGECENAC
REPLCCAC
ACROOMS
USECENAC
THERMAINAC
PROTHERMAC
AUTOCOOLNITE
AUTOCOOLDAY
TEMPHOMEAC
TEMPGONEAC
TEMPNITEAC
NUMBERAC
WWACAGE
ESWWAC
REPLCWWAC
USEWWAC
NUMCFAN
USECFAN
TREESHAD
NOTMOIST
USENOTMOIST
SWIMPOOL
POOL
FUELPOOL
RECBATH
FUELTUB
LGT12
LGT12EE
LGT4
LGT4EE
LGT1
LGT1EE
NOUTLGTNT
LGTOEE
NGASLIGHT
INSTLCFL
SLDDRS
DOOR1SUM
WINDOWS
TYPEGLASS
NEWGLASS
ADQINSUL
INSTLINS
AGEINS
DRAFTY
INSTLWS
AGEWS
AUDIT
AGEAUD
USEEL
USENG
USELP
USEFO
USEKERO
USEWOOD
USESOLAR
USEOTH
ELWARM
ELECAUX
ELCOOL
ELWATER
ELFOOD
ELOTHER
UGWARM
UGASAUX
UGWATER
UGCOOK
UGOTH
LPWARM
LPGAUX
LPWATER
LPCOOK
LPOTHER
FOWARM
FOILAUX
FOWATER
FOOTHER
KRWARM
KEROAUX
KRWATER
KROTHER
WDWARM
WOODAUX
WDWATER
WDOTHUSE
SOLWARM
SOLARAUX
SOLWATER
SOLOTHER
OTHWARM
OTHERAUX
OTHWATER
OTHCOOK
ONSITE
ONSITEGRID
PELHEAT
PELHOTWA
PELCOOK
PELAC
PELLIGHT
OTHERWAYEL
PGASHEAT
PGASHTWA
PUGCOOK
PUGOTH
OTHERWAYNG
FOPAY
OTHERWAYFO
LPGPAY
OTHERWAYLPG
LPGDELV
KERODEL
KEROCASH
NOCRCASH
NKRGALNC
WOODLOGS
WDSCRAP
WDPELLET
WDOTHER
WOODAMT
NUMCORDS
KFUELOT
HHSEX
EMPLOYHH
SPOUSE
SDESCENT
Householder_Race
EDUCATION
NHSLDMEM
HHAGE
AGEHHMEMCAT2
AGEHHMEMCAT3
AGEHHMEMCAT4
AGEHHMEMCAT5
AGEHHMEMCAT6
AGEHHMEMCAT7
AGEHHMEMCAT8
AGEHHMEMCAT9
AGEHHMEMCAT10
AGEHHMEMCAT11
AGEHHMEMCAT12
AGEHHMEMCAT13
AGEHHMEMCAT14
HBUSNESS
ATHOME
TELLWORK
TELLDAYS
OTHWORK
WORKPAY
MONEYPY
POVERTY100
POVERTY150
HUPROJ
RENTHELP
TOTSQFT
TOTSQFT_EN
TOTHSQFT
TOTUSQFT
TOTCSQFT
TOTUCSQFT
KWH
KWHSPH
KWHCOL
KWHWTH
KWHRFG
KWHOTH 
BTUEL
BTUELSPH
BTUELCOL
BTUELWTH
BTUELRFG
BTUELOTH
DOLLAREL
DOLELSPH
DOLELCOL
DOLELWTH
DOLELRFG
DOLELOTH
CUFEETNG
CUFEETNGSPH
CUFEETNGWTH
CUFEETNGOTH
BTUNG
BTUNGSPH
BTUNGWTH
BTUNGOTH
DOLLARNG
DOLNGSPH
DOLNGWTH
DOLNGOTH
GALLONLP
GALLONLPSPH
GALLONLPWTH
GALLONLPOTH
BTULP
BTULPSPH
BTULPWTH
BTULPOTH
DOLLARLP
DOLLPSPH
DOLLPWTH
DOLLPOTH
GALLONFO
GALLONFOSPH
GALLONFOWTH
GALLONFOOTH
BTUFO
BTUFOSPH
BTUFOWTH
BTUFOOTH
DOLLARFO
DOLFOSPH
DOLFOWTH
DOLFOOTH
GALLONKER
GALLONKERSPH
GALLONKERWTH
GALLONKEROTH
BTUKER
BTUKERSPH
BTUKERWTH
BTUKEROTH
DOLLARKER
DOLKERSPH
DOLKERWTH
DOLKEROTH
BTUWOOD
CORDSWD
TOTALBTU
TOTALBTUSPH
TOTALBTUCOL
TOTALBTUWTH
TOTALBTURFG
TOTALBTUOTH
TOTALDOL
TOTALDOLSPH
TOTALDOLCOL
TOTALDOLWTH
TOTALDOLRFG
TOTALDOLOTH


Putting them all in one place so I can deal with them algorymically. 
```{r}


# Names2009 just contains the 2009 variable names we want
Cols2009<-read.table("Names2009.csv")
Cols2009$Status<-"Uncoded"
source("RECSHelper.R")

```



```{r}

All2009$DOEID<-as.factor(All2009$DOEID)
MarkCoded("UR")

#Region 



table(All2009$REGIONC)

All2009$REGIONC<-recode(All2009$REGIONC,c("1"="NE","2"="Midwest","3"="South","4"="West"))

summary(All2009$REGIONC)
MarkCoded("REGIONC")


#Division

table(All2009$DIVISION)

All2009$DIVISION<-recode(All2009$DIVISION,c("1"="NewEnglandD","2"="MidAtlantic","3"="EastNorthCent","4"="WestNorthCent","5"="SouthAtlantic","6"="EastSouthCent","7"="WestSountCent","8"="MountNorthSub","9","MountSouthSub","10"="Pacific"))

MarkCoded("DIVISION")


#Reportable_Domain

table(All2009$REPORTABLE_DOMAIN)

All2009$REPORTABLE_DOMAIN<-recode(All2009$REPORTABLE_DOMAIN,c("1"="CT.ME.NH.RI.VT","2"="MA","3"="NY","4"="NJ","5"="PA","6"="IL","7"="IN.OH","8"="MI","9"="WI","10"="IA.MN.ND.SD","11"="KS.NE","12"="MO","13"="VA","14"="DE.DC.MA.WV","15"="GA","16"="NC.SC","17"="FL","18"="AL.KY.MS","19"="TN","20"="AR.LA.OK","21"="TX","22"="CO","23"="ID.MT.UT.WY","24"="AZ","25"="NV.NM","26"="CA","27"="AK.HI.OR.WA"))

MarkCoded("REPORTABLE_DOMAIN")

# TYPEHUQ

All2009$TYPEHUQ<-recode(All2009$TYPEHUQ,c("1"="Mobile","2"="SingleDetach","3"="SingleAttach","4"="Apartment2-4Units","5"="Apartment5PlusUnits"))

summary(All2009$TYPEHUQ)

MarkCoded("TYPEHUQ")

#NWEIGHT (No NA values present)

summary(All2009$NWEIGHT)

summary(is.na(All2009$NWEIGHT))

MarkCoded("NWEIGHT")


#HDD65 (NO NA values present)

summary(All2009$HDD65)

summary(is.na(All2009$HDD65))

MarkCoded("HDD65")

#CDD65 (No NA values present)

summary(All2009$CDD65)

summary(is.na(All2009$CDD65))

MarkCoded("CDD65")

#Climate_Region_Pub


All2009$Climate_Region_Pub<-recode(All2009$Climate_Region_Pub,c("1"=" VeryCold/Cold","2"="HotDry/MixedDry","3"="HotHumid","4"="MixedHumid","5"="Marine"))

summary(All2009$Climate_Region_Pub)



#AIA_ZONE issue with revalue producing results

All2009$AIA_ZONE<-recode(All2009$AIA_Zone,c("1"="LT2000CDDGT7000HDD","2"="LT2000CDDAnd5500-7000HDD","3"="LT2000CDDAnd4000-5499HDD","4"="LT2000CDDLT4000DD","5"="GT2000CDDLT4000HDD"))

summary(All2009$AIA_ZONE)

#METROMICRO (No NA values)

summary(is.na(All2009$METROMICRO))

MarkCoded("METROMICRO")

#UR

All2009$UR<-recode(All2009$UR,c("U"="Urban","R"="Residential"))

summary(All2009$UR)

#KOWNRENT

All2009$KOWNRENT<-recode(All2009$KOWNRENT,
                          c("1"="Ownded","2"="Rented","3"="Occupied"))

summary(All2009$KOWNRENT)

#CONDCOOP  


All2009$CONDCOOP<-recode(All2009$CONDCOOP,
                          c("1"="Condo","2"="Cooperative","-2"=NA))

summary(All2009$CONDCOOP)

#YEARMADE - Numeric years seem applicable, advise if change needed
summary(All2009$YEARMADE)
MarkCoded("YEARMADE")


#YEARMADERANGE

All2009$YEARMADERANGE<-recode(All2009$YEARMADERANGE,c("1"="PRE1950","2"="1950To59","3"="1960To69","4"="1970To79","5"="1980To89","6"="1990To99","7"="2000To04","8"="2005To09"))

summary(All2009$YEARMADERANGE)


#OCCUPYRANGE

All2009$OCCUPYYRANGE<-recode(All2009$OCCUPYYRANGE,c("1"="PRE1950","2"="1950To59","3"="1960To69","4"="1970To79","5"="1980To89","6"="1990To99","7"="2000To04","8"="2005To09"))

summary(All2009$OCCUPYYRANGE)

#Conversion

All2009$CONVERSION<-recode(All2009$CONVERSION,c("1"="BuiltAsApart","2"="ConverToApart","-2"=NA))
summary(All2009$CONVERSION)



#ORIG1FAM

All2009$ORIG1FAM<-recode(All2009$ORIG1FAM,c("1"=TRUE,"0"=FALSE,"-2"=NA))

summary(All2009$ORIG1FAM)

#LOOKLIKE


All2009$LOOKLIKE<-recode(All2009$LOOKLIKE,c("1"="MoreLikeHouse","2"="MoreLikeApart","-2"=NA))


summary(All2009$LOOKLIKE)

#NUMFLRS

All2009$NUMFLRS<-recodeNumeric(All2009$NUMFLRS)


summary(All2009$NUMFLRS)


#NUMAPTS

table(All2009$NUMAPTS)

#NUMAPTS  Every value is accounted for in the table however when I look at the
#summary there is 9 values labled as 'other'.  I went throught the entire 
#column and could not find any such values that do not match the code or table.
#NOTE: The NA values match the '-2' values

# All2009$NUMAPTS<-revalue(as.factor(All2009$NUMAPTS),c("5"="5units","6"="6units","7"="7units","8"="8units","9"="9units","10"="10units","11"="11units","12"="12units","13"="13units","14"="14units","15"="15units","16"="16units","17"="17units","18"="18units","19"="19units","20"="20units","21"="21units","22"="22units","23"="23units","24"="24units","25"="25units","26"="26units","27"="27units","28"="28units","30"="30units","31"="31units","32"="32units","33"="33units","34"="34units","35"="35units","36"="36units","37"="37units","39"="39units","40"="40units","41"="41units","42"="42units","43"="43units","44"="44units","45"="45units","46"="46units","47"="47units","48"="48units","49"="49units","50"="50units","51"="51units","52"="52units","53"="53units","54"="54units","55"="55units","56"="56units","57"="57units","58"="58units","59"="59units","60"="60units","63"="63units","64"="64units","65"="65units","66"="66units","68"="68units","70"="70units","72"="72units","75"="75units","76"="76units","80"="80units","81"="81units","84"="84units","86"="86units","88"="88units","90"="90units","95"="95units","96"="96units","99"="99units","100"="100units","102"="102units","105"="105units","108"="108units","110"="110units","112"="112units","115"="115units","116"="116units","118"="118units","120"="120units","123"="123units","125"="125units","126"="126units","130"="130units","133"="133units","135"="135units","140"="140units","141"="141units","145"="145units","150"="150units","155"="155units","160"="160units","168"="168units","170"="170units","175"="175units","178"="178units","180"="180units","187"="187units","192"="192units","199"="199units","200"="200units","313"="313units","316"="316units","322"="322units","365"="365units"))


All2009$NUMAPTS[All2009$NUMAPTS==-2]<-NA
All2009$NUMAPTS<-recodeNumeric(All2009$NUMAPTS)

MarkCoded("NUMAPTS")

#WALLTYPE
# 
# All2009$WALLTYPE<-recode(All2009$WALLTYPE,c("1"="Brick","2"="Wood","3"="Siding","4"="Stucco","5"="Composition","6"="Stone","7"="Concrete","8"="Glass","9"="Other"))
# 
# summary(All2009$WALLTYPE)

# #ROOFTYPE
# 
# All2009$ROOFTYPE[All2009$ROOFTYPE==-2]<-NA
# 
# All2009$ROOFTYPE<-recode(All2009$ROOFTYPE,c("1"="Ceramic.Clay","2"="WoodShingles.Shakes","3"="Metal","4"="Slate.SyntheticSlate","5"="CompositionShingles","6"="Asphalt","7"="ConcreteTiles","8"="Other","-2"=NA))
# 
# summary(All2009$ROOFTYPE)



#STUDIO

All2009$STUDIO<-recode(All2009$STUDIO,c("0"="NO","1"="YES","-2"=NA))

summary(All2009$STUDIO)


#NAPTFLRS

table(All2009$NAPTFLRS)

All2009$NAPTFLRS[All2009$NAPTFLRS==-2]<-NA

All2009$NAPTFLRS<-recode(All2009$NAPTFLRS,c("1"="1Floor","2"="2Floors","3"="3Floors","-2"=NA))

summary(All2009$NAPTFLRS)

#STORIES


All2009$STORIES<-recode(All2009$STORIES,c("10"="OneStory","20"="TwoStories","31"="ThreeStories","32"="FourPlusStories","40"="SplitLevel","50"="OtherType","-2"=NA))

summary(All2009$STORIES)

#TYPEHUQ4 (addition to mobile home)


All2009$TYPEHUQ4<-to.TF(All2009$TYPEHUQ4)

summary(All2009$TYPEHUQ4)


#BEDROOMS

table(All2009$BEDROOMS)

All2009$BEDROOMS[All2009$BEDROOMS==-2]<-NA
# 
# All2009$BEDROOMS<-revalue(as.factor(All2009$BEDROOMS),c("0"="NoBedrooms","1"="OneBedroom","2"="TwoBedrooms","3"="ThreeBedrooms","4"="FourBedrooms","5"="FiveBedrooms","6"="SixBedrooms","7"="SevenBedrooms","8"="EightBedrooms","9"="NineBedrooms","13"="ThirteenBedrooms"))

All2009$BEDROOMS<-as.numeric(All2009$BEDROOMS)

summary(All2009$BEDROOMS)
MarkCoded("BEDROOMS")


#NCOMBATH

table(All2009$NCOMBATH)

All2009$NCOMBATH[All2009$NCOMBATH==-2]<-NA

# All2009$NCOMBATH<-revalue(as.factor(All2009$NCOMBATH),c("0"="NoFullBath","1"="OneFullBath","2"="TwoFullBath","3"="ThreeFullBath","4"="FourFullBath","5"="FiveFullBath","6"="SixFullBath","7"="SevenFullBath","8"="EightFullBath"))

All2009$NCOMBATH<-as.numeric(All2009$NCOMBATH)
summary(All2009$NCOMBATH)
MarkCoded("NCOMBATH")


#NHAFBATH

table(All2009$NHAFBATH)

# All2009$NHAFBATH<-revalue(as.factor(All2009$NHAFBATH),c("0"="NoHalfBath","1"="OneHalfBath","2"="TwoHalfBath","3"="ThreeHalfBath","9"="NineHalfBath"))

All2009$NHAFBATH<-as.numeric(All2009$NHAFBATH)
summary(All2009$NHAFBATH)

MarkCoded("NHAFBATH")


#OTHROOMS

table(All2009$OTHROOMS)

All2009$OTHROOMS<-recodeNumeric(All2009$OTHROOMS)

summary(All2009$OTHROOMS)


#TOTROOMS

table(All2009$TOTROOMS)
                         
# All2009$TOTROOMS<-revalue(as.factor(All2009$TOTROOMS),c("1"="OneRoom","2"="TwoRooms","3"="ThreeRooms","4"="FourRooms","5"="FiveRooms","6"="SixRooms","7"="SevenRooms","8"="EightRooms","9"="NineRooms","10"="TenRooms","11"="ElevenRooms","12"="TwelveRooms","13"="ThirteenRooms","14"="FourteenRooms","15"="FifteenRooms","16"="SixteenRooms","18"="EighteenRooms","19"="NineteenRooms","21"="TwentyOneRooms","23"="TwentyThreeRooms"))

All2009$TOTROOMS<-as.numeric(All2009$TOTROOMS)

summary(All2009$TOTROOMS)

MarkCoded("TOTROOMS")


#STOVEN (Number of Stoves with oven)

table(All2009$STOVEN)

All2009$STOVEN<-recode(All2009$STOVEN,c("0"="NoStove","1"="1Stove","2"="TwoStoves","3"="ThreeStoves"))

summary(All2009$STOVEN)

#STOVENFUEL (Fuel used by most frequently used stove)

All2009$STOVENFUEL<-recode(All2009$STOVENFUEL,c("1"="NaturalGas","2"="Propane/LPG","5"="Electricity","21"="OtherFuel","-2"=NA))

summary(All2009$STOVENFUEL)


#STOVE Number of sepeate cooktops

table(All2009$STOVE)

All2009$STOVE<-recode(All2009$STOVE,c("0"="ZeroCookTops","1"="OneCookTop","2"="TwoCookTops"))

summary(All2009$STOVE)

#STOVEFUEL

All2009$STOVEFUEL<-recode(All2009$STOVEFUEL,c("1"="NaturalGas","2"="Propane/LPG","5"="Electricity","21"="OtherFuel","-2"=NA))

summary(All2009$STOVEFUEL)

#OVEN

table(All2009$OVEN)

All2009$OVEN<-recode(All2009$OVEN,c("0"="NoOven","1"="OneOven","2"="TwoOvens","3"="ThreeOvens"))

summary(All2009$OVEN)

#OVENFUEL 

All2009$OVENFUEL<-recode(All2009$OVENFUEL,c("1"="NaturalGas","2"="Propane/LPG","5"="Electricity","21"="OtherFuel","-2"=NA))

summary(All2009$OVENFUEL)



#OVENUSE


All2009$OVENUSE<-recode(All2009$OVENUSE,c("0"="NotUsed","1"="3Plus/Day","2"="Two/Day","3"="Once/Day","4"="Few/Week","5"="Once/Week","6"="LessThanOnce/Week","-2"=NA))

summary(All2009$OVENUSE)

#MICRO (Microwave Used)

All2009$MICRO<-recode(All2009$MICRO,c("0"="NO","1"="YES"))

summary(All2009$MICRO)



#AMTMICRO

All2009$AMTMICRO<-recode(All2009$AMTMICRO,c("1"="Cook/ReheatMostMeals","2"="Cook/ReheasHalfMeals","3"="Cook/ReheatFewMeals","4"="UsedVeryLittle","-2"=NA))

summary(All2009$AMTMICRO)

#OUTGRILL

All2009$OUTGRILL<-recode(All2009$OUTGRILL,c("0"="NO","1"="YES"))

summary(All2009$OUTGRILL)

#OUTGRILLFUEL


All2009$OUTGRILLFUEL<-recode(All2009$OUTGRILLFUEL,c("1"="NaturalGas","2"="Propane/LPG","21"="OtherFuel","-2"=NA))

summary(All2009$OUTGRILLFUEL)


#TOASTER

All2009$TOASTER<-recode(All2009$TOASTER,c("0"="NO","1"="YES"))

summary(All2009$TOASTER)




#NUMMEAL

All2009$NUMMEAL<-recode(All2009$NUMMEAL,c("0"="NeverCooks","1"="ThreePlusTimes/Day","2"="TwoTimes/Day","3"="Once/Day","4"="FewTimes/Week","5"="Once/Week","6"="LessThanOnce/Week"))

summary(All2009$NUMMEAL)


#FUELFOOD


All2009$FUELFOOD<-recode(All2009$FUELFOOD,c("1"="NaturalGas","2"="Propane/LPG","5"="Electricity","21"="OtherFuel","-2"=NA))

summary(All2009$FUELFOOD)


#NUMFRIG

table(All2009$NUMFRIG)

# All2009$NUMFRIG<-revalue(as.factor(All2009$NUMFRIG),c("0"="NoFridege","1"="OneFridge","2"="TwoFridge","3"="ThreeFridge","4"="FourFidge","5"="FiveFridge","6"="SixFridge","7"="SevenFridge"))

All2009$NUMFRIG<-recodeNumeric(All2009$NUMFRIG)
summary(All2009$NUMFRIG)

#TYPERFR1

All2009$TYPERFR1<-recode(All2009$TYPERFR1,c("1"="Fullsize/OneDoor","3"="Halfsize/Compact","4"="Otherkind","5"="Fullsize/ThreePlusDoors","21"="FullsizeTwoDoors/FreezerNext","22"="FullsizeTwoDoors/FreezerAbove","23"="FullsizeTwodoors/Freezerbelow","-2"=NA))

summary(All2009$TYPERFR1)



#SIZRFRI1


All2009$SIZRFRI1<-recode(All2009$SIZRFRI1,c("1"="Halfsize/Compact","2"="Small","3"="Medium","4"="Large","5"="VeryLarge","-2"=NA))

summary(All2009$SIZRFRI1)

#REFRIFT1 (Defrosting Type of most commonly used fridge)


All2009$REFRIGT1<-recode(All2009$REFRIGT1,c("1"="Manual","2"="FrostFree","3"="NoWorkingFreezer","-2"=NA))

summary(All2009$REFRIGT1)




#ICE (Throught the door ice/water, most common fridge)

All2009$ICE<-recode(All2009$ICE,c("0"="NO","1"="YES","-2"=NA))

summary(All2009$ICE)

#AGERFRI1

All2009$AGERFRI1<-recode(All2009$AGERFRI1,c("1"="LessTwoYears","2"="2To4Years","3"="5To9Years","41"="10To14Years","42"="15To19Years","5"="Gr20Years","-2"=NA))

summary(All2009$AGERFRI1)

#ESFRIG

FridgeCodes<-c("0"="NO","1"="YES","-2"=NA,"-8"=NA,"-9"=NA)

All2009$ESFRIG<-recode(All2009$ESFRIG,FridgeCodes)

summary(All2009$ESFRIG)

#REPLCFRI


All2009$REPLCFRI<-recode(All2009$REPLCFRI,FridgeCodes)

summary(All2009$REPLCFRI)

#TYPERFR2


All2009$TYPERFR2<-recode(All2009$TYPERFR2,c("1"="FullsizeOneDoor","3"="HalfsizeCompact","4"="Otherkind","5"="FullsizeThreePlusDoors","21"="FullsizeTwoDoorsFreezerNext","22"="FullsizeTwoDoorsFreezerAbove","23"="FullsizeTwodoorsFreezerbelow","-2"=NA))

summary(All2009$TYPERFR2)


#SIZRFRI2


All2009$SIZRFRI2<-recode(All2009$SIZRFRI2,c("1"="Halfsize/Compact","2"="Small","3"="Medium","4"="Large","5"="VeryLarge","-2"=NA))

summary(All2009$SIZRFRI2)


#MONRFRI2

table(All2009$MONRFRI2)


All2009$MONRFRI2<-recode(All2009$MONRFRI2,c("0"="NotUsed","1"="OneMonth","2"="TwoMonths","3"="ThreeMonths","4"="FourMonths","5"="FiveMonths","6"="SixMonths","7"="SevenMonths","8"="EightMonths","9"="NineMonths","10"="TenMonths","11"="ElevenMonths","12"="TwelveMonths","-2"=NA))

summary(All2009$MONRFRI2)

#AGERFRI2


All2009$AGERFRI2<-recode(All2009$AGERFRI2,c("1"="<TwoYears","2"="2-4Years","3"="5-9Years","41"="10-14Years","42"="15-19Years","5"=">20Years","-2"=NA))

summary(All2009$AGERFRI2)





# #ESFRIG2
# 
# All2009$ESFRIG2[All2009$ESFRIG2==-2]<-NA
# All2009$ESFRIG2[All2009$ESFRIG2==-8]<-NA
# All2009$ESFRIG2[All2009$ESFRIG2==-9]<-NA
# 
# All2009$ESFRIG2<-recode(All2009$ESFRIG2,FridgeCodes)
# 
# summary(All2009$ESFRIG2)



#SEPFREEZ

All2009$SEPFREEZ<-recode(All2009$SEPFREEZ,c("0"="NO","1"="YES"))

summary(All2009$SEPFREEZ)


#NUMFREEZ


All2009$NUMFREEZ<-recodeNumeric(All2009$NUMFREEZ)

summary(All2009$NUMFREEZ)


#UPRTFRZR


All2009$UPRTFRZR<-recode(All2009$UPRTFRZR,c("1"="Upright","2"="Chest"))

summary(All2009$UPRTFRZR)

#SIZFREEZ


All2009$SIZFREEZ<-recode(All2009$SIZFREEZ,c("1"="Small","2"="Medium","3"="Large","4"="VeryLarge"))

summary(All2009$SIZFREEZ)

#REPLCFRZ

All2009$REPLCFRZ<-recode(All2009$REPLCFRZ,FridgeCodes)

summary(All2009$REPLCFRZ)


#UPRTFRZR2


All2009$UPRTFRZR2<-recode(All2009$UPRTFRZR2,c("1"="Upright","2"="Chest"))

summary(All2009$UPRTFRZR2)

#SIZFREEZ2


All2009$SIZFREEZ2<-recode(All2009$SIZFREEZ2,c("1"="Small","2"="Medium","3"="Large","4"="VeryLarge"))

summary(All2009$SIZFREEZ2)

#AGEFRZR2


All2009$AGEFRZR2<-recode(All2009$AGEFRZR2,c("1"="LeTwoYears","2"="2To4Years","3"="5To9Years","41"="10To14Years","42"="15To19Years","5"="Gr20Years"))

summary(All2009$AGEFRZR2)

#DISHWASH

All2009$DISHWASH<-recode(All2009$DISHWASH,c("0"="NO","1"="YES"))

summary(All2009$DISHWASH)

#DWASHUSE

All2009$DWASHUSE<-recode(All2009$DWASHUSE,c("11"="LeOnceWeek","12"="OnceWeek","13"="2To3Week","20"="4To6Week","30"="GrOnceDay"))

summary(All2009$DWASHUSE)



#AGEDW


All2009$AGEDW<-recode(All2009$AGEDW,c("1"="LeTwoYears","2"="2To4Years","3"="5To9Years","41"="10To14Years","42"="15To19Years","5"="Gr20Years"))

summary(All2009$AGEDW)


#ESDISHW
ExpandedMissing<-FridgeCodes

All2009$ESDISHW<-recode(All2009$ESDISHW,ExpandedMissing)

summary(All2009$ESDISHW)

#ESDISHW


All2009$ESDISHW<-recode(All2009$ESDISHW,ExpandedMissing)

summary(All2009$ESDISHW)


#REPLCDW


All2009$REPLCDW<-recode(All2009$REPLCDW,ExpandedMissing)

summary(All2009$REPLCDW)

#CWASHER

All2009$CWASHER<-recode(All2009$CWASHER,c("0"="NO","1"="YES"))

summary(All2009$CWASHER)


#TOPFRONT

All2009$TOPFRONT<-recode(All2009$TOPFRONT,c("1"="TopLoad","2"="FrontLoad"))

summary(All2009$TOPFRONT)


#WASHLOAD


All2009$WASHLOAD<-recode(All2009$WASHLOAD,c("1"="LeOneWeek","2"="2To4Week","3"="5To9Week","4"="10To14Week","5"="Gr15Week"))

summary(All2009$WASHLOAD)


#WASHTEMP

All2009$WASHTEMP<-recode(All2009$WASHTEMP,c("1"="Hot","2"="Warm","3"="Cold"))

summary(All2009$WASHTEMP)


#RNSETEMP

All2009$RNSETEMP<-recode(All2009$RNSETEMP,c("1"="Hot","2"="Warm","3"="Cold"))

summary(All2009$RNSETEMP)

#AGECWASH


All2009$AGECWASH<-recode(All2009$AGECWASH,c("1"="LeTwoYears","2"="2To4Years","3"="5To9Years","41"="10To14Years","42"="15To19Years","5"="Gr20Years"))

summary(All2009$AGECWASH)


#ESCWASH

All2009$ESCWASH<-recode(All2009$ESCWASH,ExpandedMissing)

summary(All2009$ESCWASH)


#DRYER

All2009$DRYER<-recode(All2009$DRYER,c("0"="NO","1"="YES"))

summary(All2009$DRYER)

#DRYERFUEL


All2009$DRYRFUEL<-recode(All2009$DRYRFUEL,c("1"="NG","2"="Propane","5"="Electrcity"))

summary(All2009$DRYRFUEL)

#DRYERUSE


All2009$DRYRUSE<-recode(All2009$DRYRUSE,c("1"="EveryWash","2"="Sometimes","3"="Infrequent"))

summary(All2009$DRYRUSE)


#AGECDRYER

All2009$AGECDRYER<-recode(All2009$AGECDRYER,c("1"="LeTwoYears","2"="2To4Years","3"="5To9Years","41"="10To14Years","42"="15To19Years","5"="Gr20Years"))

summary(All2009$AGECDRYER)

#TVCOLOR


All2009$TVCOLOR<-recodeNumeric(All2009$TVCOLOR)

summary(All2009$TVCOLOR)

#TVSIZE


All2009$TVSIZE1<-recode(All2009$TVSIZE1,c("1"="Le20inch","2"="21To26inch","3"="Gr37inch"))

summary(All2009$TVSIZE1)

```







```{r}

#TVTYPE1

All2009$TVTYPE1<-recode(All2009$TVTYPE1,c("1"="StandardTube","2"="LCD","3"="Plasma","4"="Projection","5"="LED","-2"=NA))

summary(All2009$TVTYPE1)

#CABLESAT1


All2009$CABLESAT1<-recode(All2009$CABLESAT1,c("0"="Neither","1"="CableBox","2"="SatelliteBox","-2"=NA))

summary(All2009$CABLESAT1)   

#COMBODVR1

All2009$COMBODVR1<-recode(All2009$COMBODVR1,c("0"="NO","1"="YES","-2"=NA))

summary(All2009$COMBODVR1)

#DVR1

All2009$DVR1<-recode(All2009$DVR1,c("0"="NO","1"="YES","-2"=NA))

summary(All2009$DVR1)

#DIGITSTB1

All2009$DIGITSTB1<-recode(All2009$DIGITSTB1,c("0"="NO","1"="YES","-2"=NA))

summary(All2009$DIGITSTB1)

#PLAYSTA1

All2009$PLAYSTA1<-recode(All2009$PLAYSTA1,c("0"="NO","1"="YES","-2"=NA))

summary(All2009$PLAYSTA1)

#COMBOVCRDVD1

All2009$COMBOVCRDVD1[All2009$COMBOVCRDVD1==-2]<-NA

All2009$COMBOVCRDVD1<-recode(All2009$COMBOVCRDVD1,c("0"="NO","1"="YES"))

summary(All2009$COMBOVCRDVD1)

#VCR1 

All2009$VCR1[All2009$VCR1==-2]<-NA

All2009$VCR1<-recode(All2009$VCR1,c("0"="NO","1"="YES"))

summary(All2009$VCR1)

#DVD1

All2009$DVD1[All2009$DVD1==-2]<-NA

All2009$DVD1<-recode(All2009$DVD1,c("0"="NO","1"="YES"))

summary(All2009$DVD1)

#TVAUDIOSYS1

All2009$TVAUDIOSYS1[All2009$TVAUDIOSYS1==-2]<-NA

All2009$TVAUDIOSYS1<-recode(All2009$TVAUDIOSYS1,c("0"="NO","1"="YES"))

summary(All2009$TVAUDIOSYS1)

#OTHERSTB1

All2009$OTHERSTB1<-recode(All2009$OTHERSTB1,c("0"="NO","1"="YES","-2"=NA))

summary(All2009$OTHERSTB1)


#TVONWD1

All2009$TVONWD1<-recode(All2009$TVONWD1,c("1"="LTOneHour","2"="1To3Hours","3"="3To6Hours","4"="6To10Hours","5"="GT5Hours","-2"=NA))

summary(All2009$TVONWD1)



```


```{r}

#TVONWDWATCH1 (Most used TV weekdays, on videogames)

All2009$TVONWDWATCH1<-recode(All2009$TVONWDWATCH1,c("0"="None","1"="All","2"="Most","3"="Half","4"="Little","-2"=NA))

summary(All2009$TVONWDWATCH1)

#TVONWE1

All2009$TVONWE1<-recode(All2009$TVONWE1,c("1"="LTOneHour","2"="1To3Hours","3"="3To6Hours","4"="6To10Hours","5"="GT5Hours","-2"=NA))

summary(All2009$TVONWE1)

#TVONWEWATCH1

All2009$TVONWEWATCH1<-recode(All2009$TVONWEWATCH1,c("0"="None","1"="All","2"="Most","3"="Half","4"="Little","-2"=NA))

summary(All2009$TVONWEWATCH1)

#TVSIZE2

All2009$TVSIZE2<-recode(All2009$TVSIZE2,c("1"="LT20inch","2"="21To26inch","3"="GT37inch","-2"=NA))

summary(All2009$TVSIZE2)

#TVTYPE2

All2009$TVTYPE2<-recode(All2009$TVTYPE2,c("1"="StandardTube","2"="LCD","3"="Plasma","4"="Projection","5"="LED","-2"=NA))

summary(All2009$TVTYPE2)

#CABLESAT2

All2009$CABLESAT2<-recode(All2009$CABLESAT2,c("0"="Neither","1"="CableBox","2"="SatelliteBox","-2"=NA))

#COMBODVR2

All2009$COMBODVR2<-recode(All2009$COMBODVR2,c("0"="NO","1"="YES"))

summary(All2009$COMBODVR2)

#DVR2

All2009$DVR2<-to.TF(All2009$DVR2)

summary(All2009$DVR2)

#DIGITSTB2

All2009$DIGITSTB2<-to.TF(All2009$DIGITSTB2)

summary(All2009$DIGITSTB2)

#PLAYSTA2

All2009$PLAYSTA2<-to.TF(All2009$PLAYSTA2)

summary(All2009$PLAYSTA2)

#COMBOVCRDVD2

All2009$COMBOVCRDVD2<-to.TF(All2009$COMBOVCRDVD2)

summary(All2009$COMBOVCRDVD2)


#VCR1 

All2009$VCR1[All2009$VCR1==-2]<-NA

All2009$VCR1<-recode(All2009$VCR1,c("0"="NO","1"="YES"))

summary(All2009$VCR1)

#DVD2


All2009$DVD2<-to.TF(All2009$DVD2)

summary(All2009$DVD2)

#TVAUDIOSYS2

All2009$TVAUDIOSYS2<-to.TF(All2009$TVAUDIOSYS1)

summary(All2009$TVAUDIOSYS2)

#OTHERSTB2

All2009$OTHERSTB2<-to.TF(All2009$OTHERSTB2)

summary(All2009$OTHERSTB2)

#TVONWD2

All2009$TVONWD2<-recode(All2009$TVONWD2,c("1"="LTOneHour","2"="1To3Hours","3"="3To6Hours","4"="6To10Hours","5"="GT5Hours","-2"=NA))

summary(All2009$TVONWD2)

#TVONWDWATCH2

All2009$TVONWDWATCH2<-recode(All2009$TVONWDWATCH2,c("0"="None","1"="All","2"="Most","3"="Half","4"="Little","-2"=NA))

summary(All2009$TVONWDWATCH2)

#TVONWE2

All2009$TVONWE2<-recode(All2009$TVONWE2,c("1"="LTOneHour","2"="1To3Hours","3"="3To6Hours","4"="6To10Hours","5"="GT5Hours","-2"=NA))

summary(All2009$TVONWE2)

#TVONWEWATCH2

All2009$TVONWEWATCH2<-recode(All2009$TVONWEWATCH2,c("0"="None","1"="All","2"="Most","3"="Half","4"="Little","-2"=NA))

summary(All2009$TVONWEWATCH2)

#NUMPC

table(All2009$NUMPC)

All2009$NUMPC<-recodeNumeric(All2009$NUMPC)

summary(All2009$NUMPC)

#PCTYPE1

All2009$PCTYPE1<-recode(All2009$PCTYPE1,c("1"="Desktop","2"="Laptop"))

summary(All2009$PCTYPE1)

#MONITOR1

All2009$MONITOR1<-recode(All2009$MONITOR1,c("0"="Standard","1"="FlatPanelLCD"))

summary(All2009$MONITOR1)


```


```{r}


#TIMEON1 (hours)

All2009$TIMEON1<-recode(All2009$TIMEON1,c("1"="LT1Hour","2"="1To3Hours","3"="3To6Hours","4"="6To10Hours","5"="GT5HOUrs","-2"=NA))

summary(All2009$TIMEON1)


#PCONOFF1

All2009$PCONOFF1<-to.TF(All2009$PCONOFF1)

summary(All2009$PCONOFF1)

#PCSLEEP1

All2009$PCSLEEP1<-to.TF(All2009$PCSLEEP1)

summary(All2009$PCSLEEP1)

#PCTYPE2

All2009$PCTYPE2<-recode(All2009$PCTYPE2,c("1"="Desktop","2"="Laptop"))

summary(All2009$PCTYPE2)

#Monitor2

All2009$MONITOR2<-recode(All2009$MONITOR2,c("0"="Standard","1"="FlatPanelLCD"))

summary(All2009$MONITOR2)

#TIMEON2

All2009$TIMEON2<-recode(All2009$TIMEON2,c("1"="LT1Hour","2"="1To3Hours","3"="3To6Hours","4"="6To10Hours","5"="GT5HOUrs"))

summary(All2009$TIMEON2)

#PCONOFF2

All2009$PCONOFF2<-to.TF(All2009$PCONOFF2)

summary(All2009$PCONOFF2)

#PCSLEEP2

All2009$PCSLEEP2<-to.TF(All2009$PCSLEEP2)

summary(All2009$PCSLEEP2)

#INTERNET

All2009$INTERNET<-to.TF(All2009$INTERNET)

summary(All2009$INTERNET)

#INDIALUP

All2009$INDIALUP<-to.TF(All2009$INDIALUP)

summary(All2009$INDIALUP)

#INDSL

All2009$INDSL<-to.TF(All2009$INDSL)

summary(All2009$INDSL)

#INCABLE

All2009$INCABLE<-to.TF(All2009$INCABLE)

summary(All2009$INCABLE)

#INSATEL

All2009$INSATEL<-to.TF(All2009$INSATEL)

summary(All2009$INSATEL)

#INWIRELESS

All2009$INWIRELESS<-recode(All2009$INWIRELESS,c("0"="NO","1"="YES","-2"=NA))

summary(All2009$INWIRELESS)

#WELLPUMP

All2009$WELLPUMP<-recode(All2009$WELLPUMP,c("0"="NO","1"="YES","-2"=NA))

summary(All2009$WELLPUMP)

#DIPSTICK

All2009$DIPSTICK<-recode(All2009$DIPSTICK,c("0"="NO","1"="YES","-2"=NA))

summary(All2009$DIPSTICK)

#SWAMPCOL

All2009$SWAMPCOL<-recode(All2009$SWAMPCOL,c("0"="NO","1"="YES","-2"=NA))

summary(All2009$SWAMPCOL)

#BATTOLS

All2009$BATTOOLS<-recode(All2009$BATTOOLS,c("1"="1To3","2"="4To8","3"="GT8"))

summary(All2009$BATTOOLS)

#BATCHRG

All2009$BATCHRG<-recode(All2009$BATCHRG,c("1"="AllTheTime","2"="AsNeeded","3"="BothWays","-2"=NA))

summary(All2009$BATCHRG)

#CHRGPLGT

All2009$CHRGPLGT<-recode(All2009$CHRGPLGT,c("0"="NO","1"="YES","2"="SomeNotAll","-2"=NA))

summary(All2009$CHRGPLGT)

#ELECDEV

All2009$ELECDEV<-recode(All2009$ELECDEV,c("1"="1To3","2"="4To8","3"="GT8"))

summary(All2009$ELECDEV)

#ELECCHRG

All2009$ELECCHRG<-recode(All2009$ELECCHRG,c("1"="AllTheTime","2"="AsNeeded","3"="BothWays","-2"=NA))

summary(All2009$ELECCHRG)


#CHRGPLGE

All2009$CHRGPLGE<-recode(All2009$CHRGPLGE,c("0"="NO","1"="YES","2"="SomeNotAll","-2"=NA))

summary(All2009$CHRGPLGE)


#DNTHEAT

All2009$DNTHEAT<-recode(All2009$DNTHEAT,c("1"="HaveHeatDontUse","2"="DontHave","-2"=NA))

summary(All2009$DNTHEAT)


#EQUIPNOHEAT

All2009$EQUIPNOHEAT<-recode(All2009$EQUIPNOHEAT,c("2"="HotWaterOrSteam","3"="CentralWarmAirFurnace","4"="HeatPump","5"="BuiltInElecUnit","6"="FloorOrPipelessFurnace","7"="BuiltInRoomHeat","8"="HeatingStove","9"="Fireplace","10"="PortableElecHeat","11"="PortableKeroseneHeat","12"="CookingStove","21"="OtherEquip","-2"=NA))

summary(All2009$EQUIPNOHEAT)


#FUELNOHEAT

All2009$FUELNOHEAT<-recode(All2009$FUELNOHEAT,c("1"="NaturalGas","2"="PropaneLPG","3"="FuelOil","4"="Kersene","5"="Electricity","7"="Wood","8"="Solar","9"="DistrictStream","21"="OtherFuel","-2"=NA))

summary(All2009$FUELNOHEAT)

MarkCoded("FUELNOHEAT")

#EQUIPM

All2009$EQUIPM<-recode(All2009$EQUIPM,c("2"="HotWaterOrSteam","3"="CentralWarmAirFurnace","4"="HeatPump","5"="BuiltInElecUnit","6"="FloorOrPipelessFurnace","7"="BuiltInRoomHeat","8"="HeatingStove","9"="Fireplace","10"="PortableElecHeat","11"="PortableKeroseneHeat","12"="CookingStove","21"="OtherEquip","-2"=NA))

summary(All2009$EQUIPM)

MarkCoded("EQUIPM")

#FUELHEAT

All2009$FUELHEAT<-recode(All2009$FUELHEAT,c("1"="NaturalGas","2"="PropaneLPG","3"="FuelOil","4"="Kersene","5"="Electricity","7"="Wood","8"="Solar","9"="DistrictStream","21"="OtherFuel","-2"=NA))

summary(All2009$FUELHEAT)


#EQUIPAGE

All2009$EQUIPAGE<-recode(All2009$EQUIPAGE,c("1"="LT2Years","2"="2TO4Years","3"="5To9Years","41"="10To14Years","42"="15To19Years","5"="GT20Years","-2"=NA))

summary(All2009$EQUIPAGE)


#REPLCHT

All2009$REPLCHT<-recode(All2009$REPLCHT,c("0"="NO","1"="YES","-2"=NA,"-8"="Refuse","-9"="DontKnow"))

summary(All2009$REPLCHT)


#HEATOTH

All2009$HEATOTH<-to.TF(All2009$HEATOTH)

summary(All2009$HEATOTH)


#EQUIPAUX

All2009$EQUIPAUX<-to.TF(All2009$EQUIPAUX)

summary(All2009$EQUIPAUX)


#REVERSE

All2009$REVERSE<-to.TF(All2009$REVERSE)

summary(All2009$REVERSE)

#WARMAIR

All2009$WARMAIR<-to.TF(All2009$WARMAIR)

summary(All2009$WARMAIR)


#FURNFUEL

All2009$FURNFUEL<-recode(All2009$FURNFUEL,c("1"="NaturalGas","2"="PropaneLPG","3"="FuelOil","4"="Kerosene","5"="Electricity","7"="Wood","8"="Solar","9"="DistrictStream","21"="OtherFuel","-2"=NA))

summary(All2009$FURNFUEL)

MarkCoded("FURNFUEL")

#STEAMR

All2009$STEAMR<-to.TF(All2009$STEAMR)

summary(All2009$STEAMR)

MarkCoded("STEAMR")

#RADFUEL

All2009$RADFUEL<-recode(All2009$RADFUEL,c("1"="NaturalGas","2"="PropaneLPG","3"="FuelOil","4"="Kerosene","5"="Electricity","7"="Wood","8"="Solar","9"="DistrictStream","21"="OtherFuel"))

summary(All2009$RADFUEL)

MarkCoded("RADFUEL")

#PERMELEC

All2009$PERMELEC<-to.TF(All2009$PERMELEC)

summary(All2009$PERMELEC)

MarkCoded("PERMELEC")

#PIPELESS

All2009$PIPELESS<-to.TF(All2009$PIPELESS)

summary(All2009$PIPELESS)

MarkCoded("PIPELESS")

#PIPEFUEL

All2009$PIPEFUEL<-recode(All2009$PIPEFUEL,c("1"="NaturalGas","2"="PropaneLPG","3"="FuelOil","4"="Kerosene","5"="Electricity","7"="Wood","8"="Solar","9"="DistrictStream","21"="OtherFuel"))

summary(All2009$PIPEFUEL)

#ROOMHEAT

All2009$ROOMHEAT<-to.TF(All2009$ROOMHEAT)

summary(All2009$ROOMHEAT)

MarkCoded("ROOMHEAT")

#RMHTFUEL

All2009$RMHTFUEL<-recode(All2009$RMHTFUEL,c("1"="NaturalGas","2"="PropaneLPG","3"="FuelOil","4"="Kerosene","-2"=NA))

summary(All2009$RMHTFUEL)

MarkCoded("RMHTFUEL")

#WOODKILN

All2009$WOODKILN<-to.TF(All2009$WOODKILN)

summary(All2009$WOODKILN)

MarkCoded("WOODKILN")

#HSFUEL

All2009$HSFUEL<-recode(All2009$HSFUEL,c("7"="Wood","21"="OtherFuel","-2"=NA))

summary(All2009$HSFUEL)

MarkCoded("HSFUEL")

#CARRYEL

All2009$CARRYEL<-to.TF(All2009$CARRYEL)

summary(All2009$CARRYEL)

MarkCoded("CARRYEL")

#CARRYKER

All2009$CARRYKER<-to.TF(All2009$CARRYKER)

summary(All2009$CARRYKER)

MarkCoded("CARRYKER")

#CHIMNEY

All2009$CHIMNEY<-to.TF(All2009$CHIMNEY)

summary(All2009$CHIMNEY)

MarkCoded("CHIMNEY")

#FPFUEL

All2009$FPFUEL<-recode(All2009$FPFUEL,c("1"="NaturalGas","2"="PropaneLPG","7"="Wood","21"="OtherFuel","-2"=NA))

summary(All2009$FPFUEL)

MarkCoded("FPFUEL")

#RANGE

All2009$RANGE<-to.TF(All2009$RANGE)

summary(All2009$RANGE)

MarkCoded("RANGE")

#RNGFUEL

All2009$RNGFUEL<-recode(All2009$RNGFUEL,c("1"="NaturalGas","2"="PropaneLPG","3"="FuelOil","4"="Kerosene","5"="Electricity","7"="Wood","21"="OtherFuel","-2"=NA))

summary(All2009$RNGFUEL)

MarkCoded("RNGFUEL")

#DIFEQUIP

All2009$DIFEQUIP<-to.TF(All2009$DIFEQUIP)

summary(All2009$DIFEQUIP)

MarkCoded("DIFEQUIP")

#DIFFUEL

All2009$DIFFUEL<-recode(All2009$DIFFUEL,c("1"="NaturalGas","2"="PropaneLPG","3"="FuelOil","4"="Kerosene","5"="Electricity","7"="Wood","8"="Solar","9"="DistrictStream","21"="OtherFuel","-2"=NA))

summary(All2009$DIFFUEL)

MarkCoded("DIFFUEL")

#EQMAMT

All2009$EQMAMT<-recode(All2009$EQMAMT,c("1"="AlmostAll","2"="AboutThreeFourths","3"="CloserToHalf","-2"=NA))

summary(All2009$EQMAMT)

MarkCoded("EQMAMT")

#HEATROOM 

All2009$HEATROOM<-recodeNumeric(All2009$HEATROOM)

summary(All2009$HEATROOM)

MarkCoded("HEATROOM")

#THERMAIN

All2009$THERMAIN<-to.TF(All2009$THERMAIN)

summary(All2009$THERMAIN)

MarkCoded("THERMAIN")

#NUMTHERM 

table(All2009$NUMTHERM)

All2009$NUMTHERM<-recodeNumeric(All2009$NUMTHERM)

summary(All2009$NUMTHERM)

MarkCoded("NUMTHERM")

#PROTHERM

All2009$PROTHERM<-to.TF(All2009$PROTHERM)

summary(All2009$PROTHERM)

MarkCoded("PROTHERM")

#AUTOHEATNITE

All2009$AUTOHEATNITE<-to.TF(All2009$AUTOHEATNITE)

summary(All2009$AUTOHEATNITE)

MarkCoded("AUTOHEATNITE")

#AUTOHEATDAY

All2009$AUTOHEATDAY<-to.TF(All2009$AUTOHEATDAY)

summary(All2009$AUTOHEATDAY)

MarkCoded("AUTOHEATDAY")

#TEMPHOME

table(All2009$TEMPHOME)

All2009$TEMPHOME<-recodeNumeric(All2009$TEMPHOME)

summary(All2009$TEMPHOME)

MarkCoded("TEMPHOME")

#TEMPGONE

All2009$TEMPGONE<-recodeNumeric(All2009$TEMPGONE)

summary(All2009$TEMPGONE)


#TEMPNITE

All2009$TEMPNITE<-recodeNumeric(All2009$TEMPNITE)

summary(All2009$TEMPNITE)


#MOISTURE

All2009$MOISTURE<-to.TF(All2009$MOISTURE)

summary(All2009$MOISTURE)


#USEMOISTURE 

All2009$USEMOISTURE<-recode(All2009$USEMOISTURE,c("1"="1to3Months","2"="4to6Months","3"="7to9Months","4"="10to11Months","5"="AllYear"))

table(All2009$USEMOISTURE)



```

```{r}

#NUMH20ONOTNK

All2009$NUMH2ONOTNK<-recodeNumeric(All2009$NUMH2ONOTNK)

summary(All2009$NUMH2ONOTNK)

#NUMH2OTHRS

All2009$NUMH2OHTRS<-recodeNumeric(All2009$NUMH2OHTRS)

summary(All2009$NUMH2OHTRS)

#H2OTYPE1

All2009$H2OTYPE1<-recode(All2009$H2OTYPE1,c("1"="StorageHeater","2"="TanklessHeater"))

summary(All2009$H2OTYPE1)

#FUELH20

All2009$FUELH2O<-recode(All2009$FUELH2O,c("1"="NaturalGas","2"="PropaneLPG","3"="FuelOil","4"="Kerosene","5"="Electricity","7"="Wood","8"="Solar","21"="OtherFuel"))

summary(All2009$FUELH2O)

#WHEATOTH

All2009$WHEATOTH<-to.TF(All2009$WHEATOTH)

summary(All2009$WHEATOTH)

#WHEATSIZ

All2009$WHEATSIZ<-recode(All2009$WHEATSIZ,c("1"="Small","2"="Medium","3"="Large"))

summary(All2009$WHEATSIZ)

#WHEATAGE

All2009$WHEATAGE<-recode(All2009$WHEATAGE, TYPEAGE)

summary(All2009$WHEATAGE)

#WHEATBKT

All2009$WHEATBKT<-to.TF(All2009$WHEATBKT)

summary(All2009$WHEATBKT)

#H2OTYPE2

All2009$H2OTYPE2<-to.TF(All2009$H2OTYPE2)

summary(All2009$H2OTYPE2)

#H2OFUEL2

All2009$FUELH2O2<-recode(All2009$FUELH2O2,c("1"="NaturalGas","2"="PropaneLPG","3"="FuelOil","4"="Kerosene","5"="Electricity","7"="Wood","8"="Solar","21"="OtherFuel"))

summary(All2009$FUELH2O2)

#WHEATSIZ2

All2009$WHEATSIZ2<-recode(All2009$WHEATSIZ2,c("1"="Small","2"="Medium","3"="Large"))

summary(All2009$WHEATSIZ2)

#WHEATAGE2

All2009$WHEATAGE2<-recode(All2009$WHEATAGE2, TYPEAGE)

summary(All2009$WHEATAGE2)

#AIRCOND

All2009$AIRCOND<-to.TF(All2009$AIRCOND)

summary(All2009$AIRCOND)

#DNTAC

All2009$DNTAC<-recode(All2009$DNTAC,c("1"="HaveButDontUse","2"="DontHave"))

summary(All2009$DNTAC)

#COOLTYPENOAC

All2009$COOLTYPENOAC<-recode(All2009$COOLTYPENOAC,c("1"="CentralAir","2"="WindowWallUnit","3"="Both"))

summary(All2009$COOLTYPENOAC)

#COOLTYPE

All2009$COOLTYPE<-recode(All2009$COOLTYPE,c("1"="CentralAir","2"="WindowWallUnit","3"="Both"))

summary(All2009$COOLTYPE)

#DUCTS

All2009$DUCTS<-to.TF(All2009$DUCTS)

summary(All2009$DUCTS)

#CENACHP

All2009$CENACHP<-to.TF(All2009$CENACHP)

summary(All2009$CENACHP)

#ACOTHERS

All2009$ACOTHERS<-to.TF(All2009$ACOTHERS)

summary(All2009$ACOTHERS)

#AGECENAC

All2009$AGECENAC<-recode(All2009$AGECENAC, TYPEAGE)

summary(All2009$AGECENAC)

#REPLCcAC

All2009$REPLCCAC<-recode(All2009$REPLCCAC,c("0"=TRUE,"1"=FALSE,"-8"=FALSE,"-9"=FALSE))

summary(All2009$REPLCCAC)

#ACROOMS

All2009$ACROOMS<-recodeNumeric(All2009$ACROOMS)

summary(All2009$ACROOMS)

#USECENAC

All2009$USECENAC<-recode(All2009$USECENAC,c("1"="FewDays","2"="FrequentUse","3"="AllSummer"))

summary(All2009$USECENAC)

#THERMAINAC

All2009$THERMAINAC<-to.TF(All2009$THERMAINAC)

summary(All2009$THERMAIN)

#PROTHERMAC

All2009$PROTHERMAC<-to.TF(All2009$PROTHERMAC)

summary(All2009$PROTHERMAC)

#AUTOCOOLNITE

All2009$AUTOCOOLNITE<-to.TF(All2009$AUTOCOOLNITE)

summary(All2009$AUTOCOOLNITE)

#AUTOCOOLDAY

All2009$AUTOCOOLDAY<-to.TF(All2009$AUTOCOOLDAY)

summary(All2009$AUTOCOOLDAY)

#TEMPHOMEAC

All2009$TEMPHOMEAC<-recodeNumeric(All2009$TEMPHOMEAC)

summary(All2009$TEMPHOMEAC)

#TEMPGONEAC

All2009$TEMPGONEAC<-recodeNumeric(All2009$TEMPGONEAC)

summary(All2009$TEMPGONEAC)

#TEMPNITEAC

All2009$TEMPNITEAC<-recodeNumeric(All2009$TEMPNITEAC)

summary(All2009$TEMPNITEAC)

#NUMBERAC

All2009$NUMBERAC<-recodeNumeric(All2009$NUMBERAC)

table(All2009$NUMBERAC)

#WWACAGE

All2009$WWACAGE<-recode(All2009$WWACAGE, TYPEAGE)

summary(All2009$WWACAGE)

#ESWWAC

summary(recode(All2009$ESWWAC,c("0"=TRUE, "1"=FALSE, "-2"=FALSE, "-8"=FALSE, "-9"=FALSE)))

#REPLACWWAC

All2009$REPLCWWAC<-recode(All2009$REPLCWWAC,c("0"=TRUE, "1"=FALSE, "-2"=FALSE, "-8"=FALSE, "-9"=FALSE))

summary(All2009$REPLCWWAC)

#USEWWAC

All2009$USEWWAC<-recode(All2009$USEWWAC,c("1"="FewDays","2"="FrequentUse","3"="AllSummer"))
        
summary(All2009$USEWWAC)

#NUMCFAN

All2009$NUMCFAN<-recodeNumeric(All2009$NUMCFAN)

summary(All2009$NUMCFAN)

#USECFAN

All2009$USECFAN<-recode(All2009$USECFAN,c("1"="FewDays","2"="FrequentUse","3"="AllSummer"))

summary(All2009$USECFAN)

#TREESHAD

All2009$TREESHAD<-to.TF(All2009$TREESHAD)

summary(All2009$TREESHAD)

#NOTMOIST

All2009$NOTMOIST<-to.TF(All2009$NOTMOIST)

summary(All2009$NOTMOIST)

#USENOTMOIST

All2009$USENOTMOIST<-recode(All2009$USENOTMOIST,c("1"="1to3Months","2"="4to6Months","3"="7to9Months","4"="10to11Months","5"="AllYear"))

summary(All2009$USENOTMOIST)

#SWIMPOOL

All2009$SWIMPOOL<-to.TF(All2009$SWIMPOOL)

summary(All2009$SWIMPOOL)

#POOL

All2009$POOL<-to.TF(All2009$POOL)

summary(All2009$POOL)

#FUELPOOL

All2009$FUELPOOL<-recode(All2009$FUELPOOL, FuelType)

summary(All2009$FUELPOOL)

#RECBATH

All2009$RECBATH<-to.TF(All2009$RECBATH)

summary(All2009)

#FUELTUB

All2009$FUELTUB<-recode(All2009$FUELTUB, FuelType)

summary(All2009$FUELTUB)

#LGT12

All2009$LGT12<-recodeNumeric(All2009$LGT12)

summary(All2009$LGT12)

# #LGT12EE (unsure how to deal with "-8", "-9")
# 
# All2009$LGT12EE<-recodeNumeric(All2009$LGT12EE)
# 
# table(All2009$LGT12EE)

#LGT4

All2009$LGT4<-recodeNumeric(All2009$LGT4)

summary(All2009$LGT4)

# #LGT4EE (unsure how to deal with "-8", "-9")
# 
# All2009$LGT4EE<-recodeNumeric(All2009$LGT4EE)
# 
# table(All2009$LGT4EE)

#LGT1

All2009$LGT1<-recodeNumeric(All2009$LGT1)

summary(All2009$LGT1)

# #LGT1EE (unsure how to deal with "-8", "-9")
# 
# All2009$LGT1EE<-recodeNumeric(All2009$LGT1EE)
# 
# table(All2009$LGT1EE)

#NOUTLGTNT

All2009$NOUTLGTNT<-recodeNumeric(All2009$NOUTLGTNT)

summary(All2009$NOUTLGTNT)

#LGTOEE

# All2009$LGTOEE<-recodeNumeric(All2009$LGTOEE)
# 
# table(All2009$LGTOEE)

#NGASLIGHT

All2009$NGASLIGHT<-recodeNumeric(All2009$NGASLIGHT)

summary(All2009$NGASLIGHT)

#INSTLCFL

All2009$INSTLCFL<-to.TF(All2009$INSTLCFL)

summary(All2009$INSTLCFL)

#SLDDRS

All2009$SLDDRS<-to.TF(All2009$SLDDRS)

summary(All2009$SLDDRS)

#DOOR1SUM

All2009$DOOR1SUM<-recodeNumeric(All2009$DOOR1SUM)

summary(All2009$DOOR1SUM)

#WINDOWS

All2009$WINDOWS<-recode(All2009$WINDOWS,c("0"="NONE","10"="1or2","20"="3or5","30"="6to9","41"="10to15","42"="16to19","50"="20to29","60"="Gr30"))

summary(All2009$WINDOWS)

#TYPEGLASS

All2009$TYPEGLASS<-recode(All2009$TYPEGLASS,c("1"="SinglePane","2"="DoublePane","3"="TriplePane"))

summary(All2009$TYPEGLASS)

#NEWGLASS

All2009$NEWGLASS<-recode(All2009$NEWGLASS,c("1"="All","2"="Some","3"="None"))

summary(All2009$NEWGLASS)

#ADWINSUL

All2009$ADQINSUL<-recode(All2009$ADQINSUL,c("1"="Well","2"="Adequate","3"="Poor","4"="None"))

summary(All2009$ADQINSUL)

#INSTLINS

All2009$INSTLINS<-to.TF(All2009$INSTLINS)

summary(All2009$INSTLINS)

#AGEINS

All2009$AGEINS<-recode(All2009$AGEINS, TYPEAGE)

summary(All2009$AGEINS)

#DRAFTY

All2009$DRAFTY<-recode(All2009$DRAFTY,c("1"="AllTime","2"="MostTime","3"="Sometime","0"="Never"))

summary(All2009$DRAFTY)

#INSTLWS

All2009$INSTLWS<-to.TF(All2009$INSTLWS)

summary(All2009$INSTLWS)

#AGEWS

All2009$AGEWS<-recode(All2009$AGEWS, TYPEAGE)

summary(All2009$AGEWS)

#AUDIT

All2009$AUDIT<-to.TF(All2009$AUDIT)

summary(All2009$AUDIT)

#AGEAUD

All2009$AGEAUD<-recode(All2009$AGEAUD, TYPEAGE)

summary(All2009$AGEAUD)

#USEEL

All2009$USEEL<-to.TF(All2009$USEEL)

summary(All2009$USEEL)

#USEENG

All2009$USENG<-to.TF(All2009$USENG)

summary(All2009$USENG)

#USELP

All2009$USELP<-to.TF(All2009$USELP)

summary(All2009$USELP)

#USEFO

All2009$USEFO<-to.TF(All2009$USEFO)

summary(All2009$USEFO)

#USEKERO

All2009$USEKERO<-to.TF(All2009$USEKERO)

summary(All2009$USEKERO)

#USEWOOD

All2009$USEWOOD<-to.TF(All2009$USEWOOD)

summary(All2009$USEWOOD)

#USESOLAR

All2009$USESOLAR<-to.TF(All2009$USESOLAR)

summary(All2009$USESOLAR)

#USEOTH

All2009$USEOTH<-to.TF(All2009$USEOTH)

summary(All2009$USEOTH)

#ELWARM

All2009$ELWARM<-to.TF(All2009$ELWARM)

summary(All2009$ELWARM)

#ELECAUX

All2009$ELECAUX<-to.TF(All2009$ELECAUX)

summary(All2009$ELECAUX)

#ELCOOL

All2009$ELCOOL<-to.TF(All2009$ELCOOL)

summary(All2009$ELCOOL)

#ELWATER

All2009$ELWATER<-to.TF(All2009$ELWATER)

summary(All2009$ELWATER)

#ELFOOD

All2009$ELFOOD<-to.TF(All2009$ELFOOD)

summary(All2009$ELFOOD)

#ELOTHER

All2009$ELOTHER<-to.TF(All2009$ELOTHER)

summary(All2009$ELOTHER)

#UGWARM

All2009$UGWARM<-to.TF(All2009$UGWARM)

summary(All2009$UGWARM)

#UGASAUX

All2009$UGASAUX<-to.TF(All2009$UGASAUX)

summary(All2009$UGASAUX)

#UGWATER

All2009$UGWATER<-to.TF(All2009$UGWATER)

summary(All2009$UGWATER)

#UGCOOK

All2009$UGCOOK<-to.TF(All2009$UGCOOK)

summary(All2009$UGCOOK)

#UGOTH

All2009$UGOTH<-to.TF(All2009$UGOTH)

summary(All2009$UGOTH)

#LPWARM

All2009$LPWARM<-to.TF(All2009$LPWARM)

summary(All2009$LPWARM)

#LPGAUX

All2009$LPGAUX<-to.TF(All2009$LPGAUX)

summary(All2009$LPGAUX)

#LPWATER

All2009$LPWATER<-to.TF(All2009$LPWATER)

summary(All2009$LPWATER)

#LPCOOK

All2009$LPCOOK<-to.TF(All2009$LPCOOK)

summary(All2009$LPCOOK)

#LPOTHER

All2009$LPOTHER<-to.TF(All2009$LPOTHER)

summary(All2009$LPOTHER)

#FOWARM

All2009$FOWARM<-to.TF(All2009$FOWARM)

summary(All2009$FOWARM)

#FOILAUX

All2009$FOILAUX<-to.TF(All2009$FOILAUX)

summary(All2009$FOILAUX)

#FOWATER

All2009$FOWATER<-to.TF(All2009$FOWATER)

summary(All2009$FOWATER)

#FOOTHER

All2009$FOOTHER<-to.TF(All2009$FOOTHER)

summary(All2009$FOOTHER)

#KRWARM

All2009$KRWARM<-to.TF(All2009$KRWARM)

summary(All2009$KRWARM)

#KEROAUX

All2009$KEROAUX<-to.TF(All2009$KEROAUX)

summary(All2009$KEROAUX)

#KRWATER

All2009$KRWATER<-to.TF(All2009$KRWATER)

summary(All2009$KRWATER)

#KROTHER

All2009$KROTHER<-to.TF(All2009$KROTHER)

summary(All2009$KROTHER)

#WDWARM

All2009$WDWARM<-to.TF(All2009$WDWARM)

summary(All2009$WDWARM)

#WOODAUX

All2009$WOODAUX<-to.TF(All2009$WOODAUX)

summary(All2009$WOODAUX)

#WDWATER

All2009$WDWATER<-to.TF(All2009$WDWATER)

summary(All2009$WDWATER)

#WDOTHUSE

All2009$WDOTHUSE<-to.TF(All2009$WDOTHUSE)

summary(All2009$WDOTHUSE)

#SOLWARM

All2009$SOLWARM<-to.TF(All2009$SOLWARM)

summary(All2009$SOLWARM)

#SOLARAUX

All2009$SOLARAUX<-to.TF(All2009$SOLARAUX)

summary(All2009$SOLARAUX)

#SOLARWATER

All2009$SOLWATER<-to.TF(All2009$SOLWATER)

summary(All2009$SOLWATER)

#SOLOTHER

All2009$SOLOTHER<-to.TF(All2009$SOLOTHER)

summary(All2009$SOLOTHER)

#OTHWARM

All2009$OTHWARM<-to.TF(All2009$OTHWARM)

summary(All2009$OTHWARM)

#OTHERAUX

All2009$OTHERAUX<-to.TF(All2009$OTHERAUX)

summary(All2009$OTHERAUX)

#OTHWATER

All2009$OTHWATER<-to.TF(All2009$OTHWATER)

summary(All2009$OTHWARM)

#OTHCOOK

All2009$OTHCOOK<-to.TF(All2009$OTHCOOK)

summary(All2009$OTHCOOK)

#ONSITE

All2009$ONSITE<-to.TF(All2009$ONSITE)

summary(All2009$ONSITE)

#ONSITEGRID

All2009$ONSITEGRID<-to.TF(All2009$ONSITEGRID)

summary(All2009$ONSITEGRID)

#PELHEAT

All2009$PELHEAT<-recode(All2009$PELHEAT, PAYMENTS)

summary(All2009$PELHEAT)

#PELHOTWA

All2009$PELHOTWA<-recode(All2009$PELHOTWA, PAYMENTS)

summary(All2009$PELHOTWA)

#PELCOOK

All2009$PELCOOK<-recode(All2009$PELCOOK, PAYMENTS)

summary(All2009$PELCOOK)

#PELAC

All2009$PELAC<-recode(All2009$PELAC, PAYMENTS)

summary(All2009$PELAC)

#PELLIGHT

All2009$PELLIGHT<-recode(All2009$PELLIGHT, PAYMENTS)

summary(All2009$PELLIGHT)

#OTHERWAYEL

All2009$OTHERWAYEL<-recode(All2009$OTHERWAYEL,c("1"="Relative","2"="RentalAgent","3"="OtherParty"))

summary(All2009$OTHERWAYEL)

#PGASHEAT

All2009$PGASHEAT<-recode(All2009$PGASHEAT, PAYMENTS)

summary(All2009$PGASHEAT)

#PGASHTWA

All2009$PGASHTWA<-recode(All2009$PGASHTWA, PAYMENTS)

summary(All2009$PGASHTWA)

#PUGCOOK

All2009$PUGCOOK<-recode(All2009$PUGCOOK, PAYMENTS)

summary(All2009$PUGCOOK)

#PUGOTH

All2009$PUGOTH<-recode(All2009$PUGOTH, PAYMENTS)

summary(All2009$PUGOTH)


#OTHERWAYG

All2009$OTHERWAYNG<-recode(All2009$OTHERWAYNG,c("1"="Relative","2"="RentalAgent","3"="OtherParty"))

summary(All2009$OTHERWAYNG)

#FOPAY

All2009$FOPAY<-recode(All2009$FOPAY, PAYMENTS)

summary(All2009$FOPAY)

#OTHERWAYFO

All2009$OTHERWAYFO<-recode(All2009$OTHERWAYFO,c("1"="Relative","2"="RentalAgent","3"="OtherParty"))

summary(All2009$OTHERWAYFO)

#LPGPAY

All2009$LPGPAY<-recode(All2009$LPGPAY, PAYMENTS)

summary(All2009$LPGPAY)

#OTHERWAYLPG

All2009$OTHERWAYLPG<-recode(All2009$OTHERWAYLPG,c("1"="Relative","2"="RentalAgent","3"="OtherParty"))

summary(All2009$OTHERWAYLPG)

#LPGDELV

All2009$LPGDELV<-to.TF(All2009$LPGDELV)

summary(All2009$LPGDELV)

#KERODEL

All2009$KERODEL<-to.TF(All2009$KERODEL)

summary(All2009$KERODEL)

#KEROCASH

All2009$KEROCASH<-to.TF(All2009$KEROCASH)

summary(All2009$KEROCASH)

#NOCRCASH

table(All2009$NOCRCASH)

All2009$NOCRCASH<-recodeNumeric(All2009$NOCRCASH)

summary(All2009$NOCRCASH)

#NKRGALNC

All2009$NKRGALNC<-recode(All2009$NKRGALNC,c("77"="NotSure"))

All2009$NKRGALNC<-recodeNumeric(All2009$NKRGALNC)

summary(All2009$NKRGALNC)

#WOODLOGS

All2009$WOODLOGS<-to.TF(All2009$WOODLOGS)

summary(All2009$WOODLOGS)

#WDSCRAP

All2009$WDSCRAP<-to.TF(All2009$WDSCRAP)

summary(All2009$WDSCRAP)

#WDPELLET

All2009$WDPELLET<-to.TF(All2009$WDPELLET)

summary(All2009$WDPELLET)

#WDOTHER

All2009$WDOTHER<-to.TF(All2009$WDOTHER)

summary(All2009$WDOTHER)

#WOODAMT (in cords)

All2009$WOODAMT<-recode(All2009$WOODAMT,c("1"="LeHalf","2"="About1","3"="About2","4"="3to5","5"="Gr5"))

summary(All2009$WOODAMT)


#NUMCORDS

All2009$NUMCORDS<-recodeNumeric(All2009$NUMCORDS)

summary(All2009$NUMCORDS)

#KFUELOT

All2009$KFUELOT<-to.TF(All2009$KFUELOT)

summary(All2009$KFUELOT)

#HHSEX

All2009$HHSEX<-recode(All2009$HHSEX,c("1"="Female","2"="Male"))

summary(All2009$HHSEX)

#EMPLOYHH

All2009$EMPLOYHH<-recode(All2009$EMPLOYHH,c("0"="NoEmplyOrRetired","1"="FullTime","2"="Partime"))

summary(All2009$EMPLOYHH)

#SPOUSE

All2009$SPOUSE<-to.TF(All2009$SPOUSE)

summary(All2009$SPOUSE)

#SDESCENT

All2009$SDESCENT<-to.TF(All2009$SDESCENT)

summary(All2009$SDESCENT)

#Household_Race 

All2009$Householder_Race<-recode(All2009$Householder_Race,c("1"="WhiteOnly","2"="AfricanAmerican","3","AmericanIndianOrAlaskaNative","4"="Asian","5"="NativeHawaiianOrPacificIsland","6"="OtherRace","7"="2OrMoreSelected"))

summary(All2009$Householder_Race)

#EDUCATION

All2009$EDUCATION<-recode(All2009$EDUCATION,c("0"="NoSchool","1"="Kto12","2"="HSDiplomaOrGED","3"="SomeCollege","4"="AssocDegree","5"="BachDegree","6"="MasterDegree","7"="ProfessionDegree","8"="DoctorateDegree"))

summary(All2009$EDUCATION)

#NHSLDMEM

All2009$NHSLDMEM<-recodeNumeric(All2009$NHSLDMEM)

summary(All2009$NHSLDMEM)

#HHAGE

All2009$HHAGE<-recode(All2009$HHAGE, AGECAT)

summary(All2009$HHAGE)

#AGEHHMEMCAT2

All2009$AGEHHMEMCAT2<-recodeNumeric(All2009$AGEHHMEMCAT2)

summary(All2009$AGEHHMEMCAT2)

#AGEHHMEMCAT3

All2009$AGEHHMEMCAT3<-recode(All2009$AGEHHMEMCAT3, AGECAT)

summary(All2009$AGEHHMEMCAT3)

#AGEHHMEMCAT4

All2009$AGEHHMEMCAT4<-recode(All2009$AGEHHMEMCAT4, AGECAT)

summary(All2009$AGEHHMEMCAT4)

#AGEHHMEMCAT5

All2009$AGEHHMEMCAT5<-recode(All2009$AGEHHMEMCAT5, AGECAT)

summary(All2009$AGEHHMEMCAT5)

#AGEHHMEMCAT6

All2009$AGEHHMEMCAT6<-recode(All2009$AGEHHMEMCAT6, AGECAT)

summary(All2009$AGEHHMEMCAT6)

#AGEHHMEMCAT7

All2009$AGEHHMEMCAT7<-recode(All2009$AGEHHMEMCAT7, AGECAT)

summary(All2009$AGEHHMEMCAT7)

#AGEHHMEMCAT8

All2009$AGEHHMEMCAT8<-recode(All2009$AGEHHMEMCAT8, AGECAT)

summary(All2009$AGEHHMEMCAT8)

#AGEHHMEMCAT9

All2009$AGEHHMEMCAT9<-recode(All2009$AGEHHMEMCAT9, AGECAT)

summary(All2009$AGEHHMEMCAT9)

#AGEHHMEMCAT10

All2009$AGEHHMEMCAT10<-recode(All2009$AGEHHMEMCAT10, AGECAT)

summary(All2009$AGEHHMEMCAT10)

#AGEHHMEMCAT11

All2009$AGEHHMEMCAT11<-recode(All2009$AGEHHMEMCAT11, AGECAT)

summary(All2009$AGEHHMEMCAT11)

#AGEHHMEMCAT12

All2009$AGEHHMEMCAT12<-recode(All2009$AGEHHMEMCAT12, AGECAT)

summary(All2009$AGEHHMEMCAT12)

#AGEHHMEMCAT13

All2009$AGEHHMEMCAT13<-recode(All2009$AGEHHMEMCAT13, AGECAT)

summary(All2009$AGEHHMEMCAT13)

#AGEHHMEMCAT14

All2009$AGEHHMEMCAT14<-recode(All2009$AGEHHMEMCAT14, AGECAT)

summary(All2009$AGEHHMEMCAT14)

#HBUSNESS

All2009$HBUSNESS<-to.TF(All2009$HBUSNESS)

summary(All2009$HBUSNESS)

#ATHOME

All2009$ATHOME<-to.TF(All2009$ATHOME)

summary(All2009$ATHOME)

#TELLWORK

All2009$TELLWORK<-to.TF(All2009$TELLWORK)

summary(All2009$TELLWORK)

#TELLDAYs

All2009$TELLDAYS<-recodeNumeric(All2009$TELLDAYS)

summary(All2009$TELLDAYS)

#OTHWORK

All2009$OTHWORK<-to.TF(All2009$OTHWORK)

summary(All2009$OTHWORK)

#WORKPAY

All2009$WORKPAY<-to.TF(All2009$WORKPAY)

summary(All2009$WORKPAY)

#MONEYPY

All2009$MONEYPY<-recode(All2009$MONEYPY,c("1"="Le2500","2"="2500To4999","3"="5000To7499","4"="7500To9999","5"="10Kto14999","6"="15Kto19999","7"="20KTo24999","8"="25KTo29999","9"="30Kto34999","10"="35KTo39999","11"="40KTo44999","12"="45KTo49999","13"="50KTo54999","14"="55KTo59999","15"="60KTo64999","16"="65KTo69999","17"="70KTO74999","18"="75KTO79999","19"="80KTo84999","20"="85KTo89999","21"="90KTo94999","22"="95KTo99999","23"="100KTo119999","24"="Gr120K"))

summary(All2009$MONEYPY)

#POVERTY100

All2009$POVERTY100<-to.TF(All2009$POVERTY100)

summary(All2009$POVERTY100)

#POVERTY150

All2009$POVERTY150<-to.TF(All2009$POVERTY150)

summary(All2009$POVERTY150)

#HUPROJ

All2009$HUPROJ<-to.TF(All2009$HUPROJ)

summary(All2009$HUPROJ)

#RENTHELP

All2009$RENTHELP<-to.TF(All2009$RENTHELP)

summary(All2009$RENTHELP)

#TOTSQFT

All2009$TOTSQFT<-recodeNumeric(All2009$TOTSQFT)

summary(All2009$TOTSQFT)

#TOTSQFT_EN

All2009$TOTSQFT_EN<-recodeNumeric(All2009$TOTSQFT_EN)

summary(All2009$TOTSQFT_EN)

#TOTHSQFT

All2009$TOTHSQFT<-recodeNumeric(All2009$TOTHSQFT)

summary(All2009$TOTHSQFT)

#TOTUSQFT

All2009$TOTUSQFT<-recodeNumeric(All2009$TOTUSQFT)

summary(All2009$TOTUSQFT)

#TOTCSQFT

All2009$TOTCSQFT<-recodeNumeric(All2009$TOTCSQFT)

summary(All2009$TOTCSQFT)

#TOTUCSQFT

All2009$TOTUCSQFT<-recodeNumeric(All2009$TOTUCSQFT)

summary(All2009$TOTUCSQFT)

#KWH

All2009$KWH<-recodeNumeric(All2009$KWH)

summary(All2009$KWH)

#KWHSPH

All2009$KWHSPH<-recodeNumeric(All2009$KWHSPH)

summary(All2009$KWHSPH)

#KWHCOL

All2009$KWHCOL<-recodeNumeric(All2009$KWHCOL)

summary(All2009$KWHCOL)

#KWHWTH

All2009$KWHWTH<-recodeNumeric(All2009$KWHWTH)

summary(All2009$KWHWTH)

#KWHRFG

All2009$KWHRFG<-recodeNumeric(All2009$KWHRFG)

summary(All2009$KWHRFG)

#KWHOTH

All2009$KWHOTH<-recodeNumeric(All2009$KWHOTH)

summary(All2009$KWHOTH)

#BTUEL

All2009$BTUEL<-recodeNumeric(All2009$BTUEL)

summary(All2009$BTUEL)

#BTUELSPH

All2009$BTUELSPH<-recodeNumeric(All2009$BTUELSPH)

summary(All2009$BTUELSPH)

#BTUELCOL

All2009$BTUELCOL<-recodeNumeric(All2009$BTUELCOL)

summary(All2009$BTUELCOL)

#BTUELWTH

All2009$BTUELWTH<-recodeNumeric(All2009$BTUELWTH)

summary(All2009$BTUELWTH)

#BTUELRFG

All2009$BTUELRFG<-recodeNumeric(All2009$BTUELRFG)

summary(All2009$BTUELRFG)

#BTUELOTH

All2009$BTUELOTH<-recodeNumeric(All2009$BTUELOTH)

summary(All2009$BTUELOTH)

#DOLLAREL

All2009$DOLLAREL<-recodeNumeric(All2009$DOLLAREL)

summary(All2009$DOLLAREL)

#DOLELSPH

All2009$DOLELSPH<-recodeNumeric(All2009$DOLELSPH)

summary(All2009$DOLELSPH)

#DOLELCOL

All2009$DOLELCOL<-recodeNumeric(All2009$DOLELCOL)

summary(All2009$DOLELCOL)

#DOLELWTH

All2009$DOLELWTH<-recodeNumeric(All2009$DOLELWTH)

summary(All2009$DOLELWTH)

#DOLELRFG

All2009$DOLELRFG<-recodeNumeric(All2009$DOLELRFG)

summary(All2009$DOLELRFG)

#DOLELOTH

All2009$DOLELOTH<-recodeNumeric(All2009$DOLELOTH)

summary(All2009$DOLELOTH)

#CUFEETNG

All2009$CUFEETNG<-recodeNumeric(All2009$CUFEETNG)

summary(All2009$CUFEETNG)

#CUFEESPH

All2009$CUFEETNGSPH<-recodeNumeric(All2009$CUFEETNGSPH)

summary(All2009$CUFEETNGSPH)

#CUFEEWTH

All2009$CUFEETNGWTH<-recodeNumeric(All2009$CUFEETNGWTH)

summary(All2009$CUFEETNGWTH)

#CUFEEOTH

All2009$CUFEETNGOTH<-recodeNumeric(All2009$CUFEETNGOTH)

summary(All2009$CUFEETNGOTH)

#BTUNG

All2009$BTUNG<-recodeNumeric(All2009$BTUNG)

summary(All2009$BTUNG)

#BTUNGSPH

All2009$BTUNGSPH<-recodeNumeric(All2009$BTUNGSPH)

summary(All2009$BTUNGSPH)

#BTUNGWTH

All2009$BTUNGWTH<-recodeNumeric(All2009$BTUNGWTH)

summary(All2009$BTUELWTH)

#BTUNGOTH

All2009$BTUNGOTH<-recodeNumeric(All2009$BTUNGOTH)

summary(All2009$BTUNGOTH)

#DOLLARNG

All2009$DOLLARNG<-recodeNumeric(All2009$DOLLARNG)

summary(All2009$DOLLARNG)

#DOLNGSPH

All2009$DOLNGSPH<-recodeNumeric(All2009$DOLNGSPH)

summary(All2009$DOLNGSPH)

#DOLNGWTH

All2009$DOLNGWTH<-recodeNumeric(All2009$DOLNGWTH)

summary(All2009$DOLNGWTH)

#DOLNGOTH

All2009$DOLNGOTH<-recodeNumeric(All2009$DOLNGOTH)

summary(All2009$DOLNGOTH)

#GALLONLP

All2009$GALLONLP<-recodeNumeric(All2009$GALLONLP)

summary(All2009$GALLONLP)

#GALLONLPSPH

All2009$GALLONLPSPH<-recodeNumeric(All2009$GALLONLPSPH)

summary(All2009$GALLONLPSPH)

#GALLONLPWTH

All2009$GALLONLPWTH<-recodeNumeric(All2009$GALLONLPWTH)

summary(All2009$GALLONLPWTH)

#GALLONLPOTH

All2009$GALLONLPOTH<-recodeNumeric(All2009$GALLONLPOTH)

summary(All2009$GALLONLPOTH)

#BTULP

All2009$BTULP<-recodeNumeric(All2009$BTULP)

summary(All2009$BTULP)

#BTULPSPH

All2009$BTULPSPH<-recodeNumeric(All2009$BTULPSPH)

summary(All2009$BTULPSPH)

#BTULPWTH

All2009$BTULPWTH<-recodeNumeric(All2009$BTULPWTH)

summary(All2009$BTULPWTH)

#BTULPOTH

All2009$BTULPOTH<-recodeNumeric(All2009$BTULPOTH)

summary(All2009$BTULPOTH)

#DOLLARLP

All2009$DOLLARLP<-recodeNumeric(All2009$DOLLARLP)

summary(All2009$DOLLARLP)

#DOLLPSPH

All2009$DOLLPSPH<-recodeNumeric(All2009$DOLLPSPH)

summary(All2009$DOLLPSPH)

#DOLLPWTH

All2009$DOLLPWTH<-recodeNumeric(All2009$DOLLPWTH)

summary(All2009$DOLLPWTH)

#DOLLPOTH

All2009$DOLLPOTH<-recodeNumeric(All2009$DOLLPOTH)

summary(All2009$DOLLPOTH)

#GALLONFO

All2009$GALLONFO<-recodeNumeric(All2009$GALLONFO)

summary(All2009$GALLONFO)

#GALLONFOSPH

All2009$GALLONFOSPH<-recodeNumeric(All2009$GALLONFOSPH)

summary(All2009$GALLONFOSPH)

#GALLONFOWTH

All2009$GALLONFOWTH<-recodeNumeric(All2009$GALLONFOWTH)

summary(All2009$GALLONFOWTH)

#GALLONFOOTH

All2009$GALLONFOOTH<-recodeNumeric(All2009$GALLONFOOTH)

summary(All2009$GALLONFOOTH)

#BTUFO

All2009$BTUFO<-recodeNumeric(All2009$BTUFO)

summary(All2009$BTUFO)

#BTUFOSPH

All2009$BTUFOSPH<-recodeNumeric(All2009$BTUFOSPH)

summary(All2009$BTUFOSPH)

#BTUFOWTH

All2009$BTUFOWTH<-recodeNumeric(All2009$BTUFOWTH)

summary(All2009$BTUFOWTH)

#BTUFOOTH

All2009$BTUFOOTH<-recodeNumeric(All2009$BTUFOOTH)

summary(All2009$BTUFOOTH)

#DOLLARFO

All2009$DOLLARFO<-recodeNumeric(All2009$DOLLARFO)

summary(All2009$DOLLARFO)

#DOLFOSPH

All2009$DOLFOSPH<-recodeNumeric(All2009$DOLFOSPH)

summary(All2009$DOLFOSPH)

#DOLFOWTH

All2009$DOLFOWTH<-recodeNumeric(All2009$DOLFOWTH)

summary(All2009$DOLFOWTH)

#DOLFOOTH

All2009$DOLFOOTH<-recodeNumeric(All2009$DOLFOOTH)

summary(All2009$DOLFOOTH)

#GALLONKER

All2009$GALLONKER<-recodeNumeric(All2009$GALLONKER)

summary(All2009$GALLONKER)

#GALLONKERSPH

All2009$GALLONKERSPH<-recodeNumeric(All2009$GALLONKERSPH)

summary(All2009$GALLONKERSPH)

#GALLONKERWTH

All2009$GALLONKERWTH<-recodeNumeric(All2009$GALLONKERWTH)

summary(All2009$GALLONKERWTH)

#GALLONKEROTH

All2009$GALLONKEROTH<-recodeNumeric(All2009$GALLONKEROTH)

summary(All2009$GALLONKEROTH)

#BTUKER

All2009$BTUKER<-recodeNumeric(All2009$BTUKER)

summary(All2009$BTUKER)

#BTUKERSPH

All2009$BTUKERSPH<-recodeNumeric(All2009$BTUKERSPH)

summary(All2009$BTUKERSPH)

#BTUKERWTH

All2009$BTUKERWTH<-recodeNumeric(All2009$BTUKERWTH)

summary(All2009$BTUKERWTH)

#BTUKEROTH

All2009$BTUKEROTH<-recodeNumeric(All2009$BTUKEROTH)

summary(All2009$BTUKEROTH)

#DOLLARKER

All2009$DOLLARKER<-recodeNumeric(All2009$DOLLARKER)

summary(All2009$DOLLARKER)

#DOLEKRSPH

All2009$DOLKERSPH<-recodeNumeric(All2009$DOLKERSPH)

summary(All2009$DOLKERSPH)

#DOLKERWTH

All2009$DOLKERWTH<-recodeNumeric(All2009$DOLKERWTH)

summary(All2009$DOLKERWTH)

#DOLKEROTH

All2009$DOLKEROTH<-recodeNumeric(All2009$DOLKEROTH)

summary(All2009$DOLKEROTH)

#BTUWOOD

All2009$BTUWOOD<-recodeNumeric(All2009$BTUWOOD)

summary(All2009$BTUWOOD)

#CORDSWD

All2009$CORDSWD<-recodeNumeric(All2009$CORDSWD)

summary(All2009$CORDSWD)

#TOTALBTU

All2009$TOTALBTU<-recodeNumeric(All2009$TOTALBTU)

summary(All2009$TOTALBTU)

#TOTALBTUSPH

All2009$TOTALBTUSPH<-recodeNumeric(All2009$TOTALBTUSPH)

summary(All2009$TOTALBTUSPH)

#TOTALBTUCOL

All2009$TOTALBTUCOL<-recodeNumeric(All2009$TOTALBTUCOL)

summary(All2009$TOTALBTUCOL)

#TOTALBTUWTH

All2009$TOTALBTUWTH<-recodeNumeric(All2009$TOTALBTUWTH)

summary(All2009$TOTALBTUWTH)

#TOTALBTURFG

All2009$TOTALBTURFG<-recodeNumeric(All2009$TOTALBTURFG)

summary(All2009$TOTALBTURFG)

#TOTALBTUOTH

All2009$TOTALBTUOTH<-recodeNumeric(All2009$TOTALBTUOTH)

summary(All2009$TOTALBTUOTH)

#TOTALDOL

All2009$TOTALDOL<-recodeNumeric(All2009$TOTALDOL)

summary(All2009$TOTALDOL)

#TOTALDOLSPH

All2009$TOTALDOLSPH<-recodeNumeric(All2009$TOTALDOLSPH)

summary(All2009$TOTALDOLSPH)

#TOTALDCOL

All2009$TOTALDOLCOL<-recodeNumeric(All2009$TOTALDOLCOL)

summary(All2009$TOTALDOLCOL)

#TOTALDOLOTH

All2009$TOTALDOLWTH<-recodeNumeric(All2009$TOTALDOLWTH)

summary(All2009$TOTALDOLWTH)

#TOTALDOLRFG

All2009$TOTALDOLRFG<-recodeNumeric(All2009$TOTALDOLRFG)

summary(All2009$TOTALDOLRFG)

#TOTALDOLOTH

All2009$TOTALDOLOTH<-recodeNumeric(All2009$TOTALDOLOTH)

summary(All2009$TOTALDOLOTH)

#

```











Now identify those that are clearly TF binary.  First look for those with only two codes

```{r}
NumberOfCodes<-apply(All2009[Cols2009$V1],MARGIN=2, FUN=function(x) length(table(x)))


OnlyTwoCodes<-names(NumberOfCodes[NumberOfCodes==2])
summary(All2009[OnlyTwoCodes])
```
Looking throught that list for things that are not TF and deleteing them from the list and recode the remaining ones to TF

```{r}
# Only one is UR.  Remove from the list.

OnlyTwoCodes<-OnlyTwoCodes[OnlyTwoCodes!="UR"]

#UR looks like it is coded
summary(All2009$UR)
Cols2009$Status[Cols2009$V1=="UR"]<-"Coded"

source("RECSHelper.R")

#modify so only does the Z type columns
# All2009[OnlyTwoCodes]<-apply(All2009[OnlyTwoCodes],MARGIN=2, FUN=function(x) to.TF(x,na.choice="KEEP"))
# 
# summary(All2009[OnlyTwoCodes])
# 
# Cols2009[is.element(Cols2009$V1,OnlyTwoCodes),]$Status<-"Coded"
```

Fixed all those in one fell swoop.

Lets check the ones with three potential codes

```{r}
# OnlyThreeCodes<-names(NumberOfCodes[NumberOfCodes==3])
# 
# summary(All2009[OnlyThreeCodes])
```
My hope is to spot those that are TF with missing.  Lets refine it so we only have numerical codes with a min of exactly -2 and a max of exactly 1.

```{r}
# #Returns true if three codes with max of 1 and min of -2
# FindTFWMissing<-function(x){
#   ret<-FALSE
#   if(length(table(x))==3 & max(x)==1 & min(x)==-2) ret<-TRUE;
#   ret
# }
# 
# #tests
# FindTFWMissing(All2009$GARGCOOL)
# FindTFWMissing(All2009$FREEZER2)
# FindTFWMissing(All2009$BASEUSE)
# summary(All2009$BASEUSE)
# 
# #Broken somehow
# table(apply(data.frame(All2009$GARGCOOL,All2009$FREEZER2,All2009$BASEUSE   ),MARGIN = 2, FUN = function(x) FindTFWMissing(x)))
# 
# table(apply(data.frame(All2009),MARGIN = 2, FUN = function(x) FindTFWMissing(x)))


```

Look for uncoded.  There are still 12 to fix. ***TODO***

```{r}

Cols2009$V1[Cols2009$Status=="Uncoded"]

table(Cols2009$Status)
```

```{r}
All2009$DOEID<-as.factor(All2009$DOEID)
MarkCoded("DOEID")



##
All2009$VCR2<-recode(All2009$VCR2,c("0"="NO","1"="YES"))

summary(All2009$VCR2)


##
All2009$TVAUDIOSYS2<-recode(All2009$TVAUDIOSYS2,c("0"="NO","1"="YES"))

summary(All2009$TVAUDIOSYS1)

##
All2009$COMPUTER<-recode(All2009$COMPUTER,c("0"="NO","1"="YES"))

summary(All2009$COMPUTER)

###
All2009$AQUARIUM<-recode(All2009$AQUARIUM,c("0"="NO","1"="YES"))

summary(All2009$AQUARIUM)

  


###
All2009$HEATHOME<-recode(All2009$HEATHOME,c("0"="NO","1"="YES"))

summary(All2009$HEATHOME)


###

All2009$LGT12EE <-recodeNumeric(All2009$LGT12EE) 
All2009$LGT12EE[All2009$LGT12EE==-8]<-NA
All2009$LGT12EE[All2009$LGT12EE==-9]<-NA
summary(All2009$LGT12EE)

###

All2009$LGT4EE <-recodeNumeric(All2009$LGT4EE) 
All2009$LGT4EE[All2009$LGT4EE==-8]<-NA
All2009$LGT4EE[All2009$LGT4EE==-9]<-NA
summary(All2009$LGT4EE)



###

All2009$LGT1EE <-recodeNumeric(All2009$LGT1EE) 
All2009$LGT1EE[All2009$LGT1EE==-8]<-NA
All2009$LGT1EE[All2009$LGT1EE==-9]<-NA
summary(All2009$LGT1EE)

###

All2009$LGTOEE <-recodeNumeric(All2009$LGTOEE) 
All2009$LGTOEE[All2009$LGTOEE==-8]<-NA
All2009$LGTOEE[All2009$LGTOEE==-9]<-NA
summary(All2009$LGTOEE)


table()
```


# RECS 2005

```{r}

#Set up with blank names
Cols2009$Names2005<-''
Cols2009$Status2005<-'Uncoded'

Cols2009$Names2005[is.element(as.character(Cols2009$V1),names(All2005))]<-as.character(Cols2009$V1)[is.element(as.character(Cols2009$V1),names(All2005))]


#redefine this function for 2005 data frame
MarkCoded<-function(nameCol){
  Cols2009[Cols2009$Names2005==nameCol,]$Status2005<<-"Coded"
  
}

```


```{r}

#NAs are coded as 9, 99, 999, etc.  Need to detect and turn to NA

NA99<-function(column){
  ret<-column
  Largest<-max(column, na.rm=TRUE)
  if(Largest%in% c(9,99,999,9999,99999,999999,9999999,99999999)){
    
    ret[ret==Largest]<-NA
  }
    
  ret
}

#Tests for the function to detect the 99999 NA codes
# table(All2005$NUMFLRS)
# table(NA99(All2005$NUMFLRS))
# summary(NA99(All2005$NUMFLRS))
# 
# table(All2005$NUMFLRS)
# table(NA99(All2005$NUMFLRS))
# 
# summary(NA99(All2005$DOEID))


All2005<-as.data.frame(apply(All2005, MARGIN = 2, NA99))
#summary(All2005)
```



Look for analogous variables in RECS205layoutAllData.csv

# RECS 2001

Code books are broken up by data file.  codebook82001.txt is for publicuse82001.csv.

Look for variables analogous to the ones in the 2009 list. 

```{r}
Cols2009$Names2001<-''
Cols2009$Status2001<-'Uncoded'

Cols2009$Names2001[is.element(as.character(Cols2009$V1),names(All2001))]<-as.character(Cols2009$V1)[is.element(as.character(Cols2009$V1),names(All2001))]


#redefine this function for 2001 data frame
MarkCoded<-function(nameCol){
  Cols2009[Cols2009$Names2001==nameCol,]$Status2001<<-"Coded"
  
}


```

```{r}
#Fix the NA 999 codes

All2001<-as.data.frame(apply(All2001, MARGIN = 2, NA99))
summary(All2001)
```

